

\section{Product or Service Description}\label{sec:prodservdesc}
\nonumsidenote{Venezuelan Hot Dogs offer hot dogs with unique Venezuelan recipes, fast service and convenience. The products are served faster than other fast food restaurants and have a strong focus on the Venezuelan community in the Doral area. They also have strong packaging and convenience features that set them apart from competitors. The internal strengths of the company include a unique recipe, while weaknesses include lack of capital. External opportunities include people looking for new innovative tastes, while external threats include economic recession and high competition.}

Venezuelan Hot Dogs offers two types of hot dogs: Hot Dog 1 and Hot Dog 2. Both products meet customer needs by providing great taste, fast service and convenience. Additionally, they are designed to appeal to the local Venezuelan community in the Doral area with their unique recipes. This gives them a competitive advantage over other fast food restaurants in terms of quality and service. 

The key features of these products include great taste, convenience, local adaptation for Venezuelans living in the area, as well as strong packaging that ensures freshness and quality control standards are met every time. Furthermore, customers can expect fast service due to efficient operational processes such as manufacturing, fulfillment and customer service which all help ensure orders are fulfilled quickly without compromising on quality or freshness. 

In order to capitalize on these strengths while addressing weaknesses like lack of capital, Venezuelan Hot Dogs plans to implement marketing strategies focused on targeting their local Venezuelan community through social media campaigns, digital campaigns, word-of-mouth advertising as well as fliers distributed at malls in the area. Additionally they plan to differentiate themselves from competitors by focusing more heavily on their local audience with great packaging design that appeals directly to them along with special offers targeted specifically at this demographic group . 

Their pricing strategy will be slightly higher compared to other fast food chains but still competitive enough so that customers feel it is worth it given the quality they receive along with quick delivery times . Products will be distributed mainly through their own store located in Sawgrass Mall however they do plan on expanding this number up to 6 stores throughout the Doral Area within one year followed by expansion into Miami after that .  As far as Human Resources go , currently there is 10 employees working at Venezuelean Hotdogs however there is plans for hiring family members from within the venezuelan community if needed . Finally , operational processes such as inventory management , supply chain management etc will be managed efficiently using an small storage space located near their main store where they can keep frozen foods ready for purchase each week based off sales analysis .  

