\section{Marketing and Sales Strategy}\label{sec:marketing}

Venezuelan Hot Dogs aims to sell gourmet hot dogs in the Doral area, with a focus on the local Venezuelan community. Our target market is individuals who are looking for new and innovative taste experiences. We plan to reach our target market through social media, digital campaigns, word-of-mouth, and fliers in the mall.

Our pricing strategy will be higher than that of other fast food restaurants in the area due to our focus on quality ingredients and unique recipe. The product will be distributed through our sales point located in the food corner of Sawgrass Mall.

To differentiate ourselves from competitors, we will focus on packaging and convenience while serving faster than other fast food restaurants. Our human resources policy includes hourly employees with basic benefits as per law. We plan to hire friends and family within the Venezuelan community for workforce expansion.

We have plans to expand our facilities by opening six more stores in the Doral area within a year followed by six stores per year in Miami. Our current operational processes include sourcing three suppliers for sausage, one supplier for bread, and purchasing all sauces and other ingredients from Costco.

In order to capitalize on our strengths such as unique recipe and Venezuelan community presence while addressing weaknesses such as lack of capital, we plan to implement marketing and communication campaigns focused solely on targeting Venezuelans living in Doral. This can help us build brand recognition among this specific demographic which can lead to increased sales volume.

Overall, we believe that by focusing on quality ingredients combined with excellent customer service catering specifically towards Venezuelans living in Doral; we can create a successful business model that meets both short-term goals such as selling 4MM hot dogs while also expanding into five branches long-term.