 

Venezuelan Hot Dogs is a business founded by Lucas four years ago, which offers two types of hot dogs: hot dog 1 and hot dog 2. The company's goal is to become the leading fast food provider in Doral, Florida. The target market of the company is the people living in Doral, with a competitive advantage based on quality and services. To achieve this goal, Venezuelan Hot Dogs will focus on targeting its primary market - Venezuelans living in Doral - through various channels such as advertising, social media campaigns, direct sales or word-of-mouths; setting a high price point but offering great packaging and convenience that sets it apart from competitors; managing human resources through hiring friends/family from Venezuelan Community; establishing operational processes such as three suppliers for sausage plus one supplier for bread; managing inventory via analyzing sales each week plus purchases made accordingly every week too; expanding facilities to up to 6 stores within next year plus more stores throughout Miami area eventually. 

The short-term goal of Venezuelan Hot Dogs is to sell 4MM annually and have 5 branches in Miami by 2021. To reach this goal, the marketing strategy will focus on targeting the Venezuelan community in Doral through various channels such as advertising, social media campaigns, direct sales or word-of-mouths. A high price will be set for fast food sector while product distribution will be done at the food corner in Sawgrass Mall. Differentiation from competitors will be achieved by focusing on the Venezuelan community with great packaging and convenience as well as served faster than other fast food restaurants. As for human resources management 10 employees are currently employed while hiring plans involve friends and family from Venezuelan Community who can help grow the business further. 

In terms of operations management one small facility has been established to prepare food in Doral while another small store can be found at Sawgrass Mall. Operational processes include three suppliers for sausage (one local supplier), one supplier for bread (local) while all sauces are bought from Costco (national). Inventory management involves analyzing sales per week with purchases made accordingly every week too so that there’s enough stock available when needed without overstocking either way which would result into losses due to wastage or outdating products respectively if not managed properly. 

 Finally expansion plans involve up to 6 stores within next year plus more stores throughout Miami area eventually so that more customers could benefit from what they offer: quality products along with great customer service which makes them stand out amongst their competition within same industry sector – Fast Food Restaurants & Cafes