.

Venezuelan Hot Dogs is a Limited Liability Company that has been in operation for four years. The key members of its management team are Lucas - President, Raul – Vice President, and Andres – Operations Manager. It offers two types of hot dogs: “Hot Dog 1” and “Hot Dog 2” which meet customer needs through taste, convenience, and local adaptation for those within the Venezuelan community who may be looking for something familiar yet innovative at the same time. Venezuelan Hot Dogs' main competitors are all the food restaurants in the Sawgrass Mall with an estimated market size of 30 billion dollars. The current market demand for their products or services is high due to full malls, while trends within their industry suggest people eating healthy food and fast food as well as low prices and supply chain pressures due to only one bread supplier. Their main sources of competitive pressure come from price competition, product differentiation, and marketing strategies employed by larger chains such as McDonalds or Wendy’s. Bargaining power of suppliers is high but buyers have no bargaining power due to the lack thereof on their part. There is also a threat from new entrants into their industry every day as well as substitutes offering new healthy options which could take away customers from Venezuelan Hot Dogs if they do not adjust accordingly. 

The company's short-term goal is to sell 4 million hot dogs while its long-term goal is to have five branches in total. To achieve this goal they need to capitalize on strengths/opportunities while addressing weaknesses/threats through marketing campaigns focused on targeting the Venezuelan community living within Doral specifically so that they know about what this business has to offer them compared with others nearby that may offer similar items but at lower prices or better quality depending on what each individual customer values most when making purchasing decisions related specifically towards what type of product/service they desire most out of any given option available in close proximity . Furthermore , it would be beneficial if Venezuelan Hot Dogs could build relationships with other businesses near them who may be interested in selling their hotdogs or providing additional services that can benefit both parties involved . This will further increase brand awareness among potential customers , allowing more people to become aware of what this business has to offer . Finally , cost efficiency should also be taken into consideration when making decisions regarding expansion plans or other strategic objectives pursued by this company so that it can remain competitive against others operating within this space .