

\section{Operations}\label{sec:operations}

\nonumsubsection{Current Size and Capacity of Physical Facilities} Venezuelan Hot Dogs currently has two physical facilities. The first is a small kitchen in the Doral area to prepare the food, and the second is a small store located in the Sawgrass Mall. 

The current size and capacity of these facilities are sufficient for Venezuelan Hot Dogs' current operations. However, plans are in place to expand the number of locations in order to reach more customers and increase sales. 

\nonumsubsection{Operational Processes} Venezuelan Hot Dogs has three suppliers for its sausages, one supplier for its bread, and all sauces and other ingredients are purchased from Costco. All ingredients are then prepared at the kitchen facility in Doral before being sent to the store at Sawgrass Mall where they can be sold directly to customers or used as part of catering services. 

\nonumsubsection{Inventory Management \& Supply Chain Management} Venezuelan Hot Dogs has an area dedicated for storing frozen food items such as sausages and breads. This helps maintain freshness while also reducing waste due to spoilage or expiration dates passing by without being used up. Purchases are made on a weekly basis based on sales data from that week so that there is always enough stock available without overstocking or understocking any particular item. 

 \nonumsubsection{Summary} Venezuelan Hot Dogs currently operates two physical facilities - a small kitchen in Doral used for preparing food items, and a store located in Sawgrass Mall where customers can purchase products directly or take advantage of catering services offered by Venezuelan Hot Dogs. The company also has three suppliers for its sausages, one supplier for its breads, with all other ingredients coming from Costco; it also maintains an area dedicated solely to storing frozen food items so that freshness is maintained while reducing waste due to spoilage or expiration dates passing by without being used up; purchases are made on a weekly basis based on sales data from that week so that there is always enough stock available without overstocking or understocking any particular item; plans are also currently underway to expand operations into more locations throughout Miami-Dade County so as to reach out even further into potential customer bases while increasing overall revenue streams through additional locations