 

Venezuelan Hot Dogs is a business founded by Lucas and located in Caracas, Venezuela. The business offers two types of hot dogs, “Hot Dog 1” and “Hot Dog 2”, both gourmet hot dogs. These products are tailored specifically to Venezuelans living abroad or within Venezuela itself due to their taste, convenience and local adaptation offerings. The target market consists of people living in the Doral area with a competitive advantage lying in the quality and services offered. Venezuelan Hot Dogs has been operational for four years now with five employees working at this business with an annual revenue of 30 billion dollars. It was founded in New York City as a small point of sale for hotdogs that has since grown into a successful business operating out of Caracas, Venezuela. 

The main competitors include all food restaurants located within the Sawgrass Mall; estimated to be around 30 billion dollars per year. There is high demand for Venezuelan Hot Dogs’ products or services due to their taste, convenience and local adaptation offerings tailored specifically towards Venezuelans living abroad or within Venezuela itself. Some challenges facing this industry include high competition from large chains such as McDonalds or Wendies; low prices; supply chain issues; price competition; product differentiation; marketing pressures; increased bargaining power from suppliers due to limited options available; lack of bargaining power from buyers due to no alternatives available; threat from new entrants into the market every day; potential substitute offerings such as healthier options on the rise; external opportunities such as new markets or partnerships that could be capitalized upon if explored properly ; external threats such as economic downturns or regulatory changes that could affect operations negatively if not monitored closely enough ; internal strengths including unique recipes/products/services offered alongside strong brand recognition/skilled workforce employed at VHD ; internal weaknesses including limited resources/weak brand recognition/lack of differentiation between VHD’s offerings compared to competitors . 

The short-term goal is to sell 4 million hot dogs and have 5 branches while the long-term goal is to expand further throughout South America. Key members of its management team are Lucas (President), Raul (Vice President) and Andres (Operations Manager). Venezuelan Hot Dogs operates as a Limited Liability Company (LLC). In order to achieve these goals, it will focus on providing high quality customer service along with efficient production processes while continuing its commitment towards innovation and improvement through research & development initiatives which can help them stay ahead of their competition in terms of product offering & pricing strategies