.

Venezuelan Hot Dogs is a limited liability company that offers gourmet hot dogs with unique recipes to customers in the Doral area. It has achieved annual revenue of $4 million since its establishment four years ago, and is looking to expand by opening five more branches in different locations around Miami. To achieve these goals, it plans on marketing campaigns targeting the Venezuelan community living in the Doral area through social media, digital campaigns, word-of-mouth advertising, and fliers distributed at malls nearby. 

The market for Venezuelan Hot Dogs' products are large with an estimated size of $30 billion dollars; however there is high competition from other fast food restaurants such as McDonalds or Wendy's which offer lower prices than Venezuelan Hot Dogs does due to their larger scale operations. To differentiate itself from competitors, Venezuelan Hot Dogs focuses on its unique recipe tailored towards local tastes within Venezuela while also providing convenience with faster service times compared to other fast food restaurants; this strategy has proven successful thus far resulting in increased sales year-on-year since establishment four years ago. Additionally, they plan on expanding their physical facilities by opening up six more stores within one year allowing them access to new markets while increasing brand visibility. 

To ensure continued success they have implemented HR policies including benefits packages, time off, performance evaluations etc., as well as training programs for employees so that they can meet standards set out by management. Furthermore they plan on managing inventory through weekly purchases based off sales data collected during that week; this allows them flexibility when dealing with sudden changes in demand for certain items. Finally pricing strategies are being formulated alongside differentiated product offerings tailored towards local tastes within Venezuela in order to capitalize on opportunities present within the industry whilst addressing weaknesses and threats posed against it; by doing so they hope to maintain customer loyalty whilst increasing sales numbers thus achieving their long term goals outlined earlier .