\section{Market Analysis}
\label{sec:market_analysis}

In this chapter, we will analyze the market for Alpha Project, including its competitors, size of the market, current demand for our products or services, challenges facing the industry, main sources of competitive pressure in the industry, bargaining power of suppliers and buyers in the industry, threat of new entrants and substitutes.

\subsection{Competitors}
Our main competitors are all food restaurants in Sograss Mall. This includes both fast food chains and sit-down restaurants. However, we believe that our unique menu offerings and emphasis on healthy options will set us apart from our competitors.

\subsection{Market Size}
The size of our market is estimated to be around 30 billion dollars. This includes all food sales within Sograss Mall as well as nearby areas.

\subsection{Current Market Demand}
There is a high demand for food within Sograss Mall as it is a popular destination for shoppers and tourists alike. All restaurants within the mall are typically full during peak hours.

\subsection{Challenges Facing the Industry}
The main challenges facing our industry include high competition from other restaurants within the mall as well as low prices due to price wars between competitors. Additionally, there may be supply chain issues with obtaining fresh ingredients on a regular basis.

\subsection{Main Competitors in Our Industry}
The main competitors in our industry are large fast food chains such as McDonald's and Wendy's. These chains have established brand recognition and loyal customer bases which can make it difficult for smaller businesses to compete.

\subsection{Sources of Competitive Pressure}
The main source of competitive pressure in our industry is price competition. Customers are often looking for affordable meal options which can lead to price wars between competing businesses.

\subsection{Bargaining Power of Suppliers}
The bargaining power of suppliers in our industry is high due to there being only one bread supplier available in Sograss Mall. This can lead to higher prices for bread products.

\subsection{Bargaining Power of Buyers}
There is no bargaining power for buyers in our industry as they are typically looking for affordable meal options and do not have the ability to negotiate prices with restaurants.

\subsection{Threat of New Entrants}
The threat of new entrants in our industry is high as there are constantly new businesses opening within Sograss Mall. However, we believe that our unique menu offerings and emphasis on healthy options will set us apart from these new competitors.

\subsection{Threat of Substitutes}
The threat of substitutes in our industry comes from the availability of new healthy options. As more customers become health-conscious, they may choose to eat at other restaurants which offer healthier meal choices. However, we believe that our focus on providing a variety of healthy options will help us overcome this threat.