
Venezuelan Hot Dogs is a Limited Liability Company founded by Lucas four years ago, which offers gourmet hot dogs in the food corner of the Sawgrass Mall located in the Doral area. The company has five employees and its purpose is to provide customers with quality products and services at competitive prices while creating an enjoyable experience for them. Venezuelan Hot Dogs' target market consists of people living in the Doral area who are looking for quality and convenience when it comes to fast food. The company's short-term goal is to reach 4 million dollars in sales, while its long-term goal is to open five branches throughout Miami. 

The industry Venezuelan Hot Dogs operates in is highly competitive, with major chains such as McDonalds or Wendies dominating the market. To address this competition, Venezuelan Hot Dogs offers two types of hot dogs: Hot Dog 1 and Hot Dog 2; these products meet customers' needs by providing them with taste, speed and convenience when eating out; they also stand out from competitors due to their unique recipes that incorporate local ingredients from Venezuela into their dishes - something no other chain can offer! Furthermore, some key features that set these hot dogs apart include their great taste and convenient packaging; moreover they are served faster than any other fast food restaurant in town!  

To remain successful against competitors, Venezuelan Hot Dogs plans on implementing several strategies including targeting their marketing efforts towards Venezuelans living abroad (via social media campaigns), offering discounts/promotions during economic downturns, investing into research & development projects that would allow them create new recipes better suited towards local tastes etc… Additionally they will focus on differentiating their products through packaging design & customer service excellence – something smaller businesses can do better than larger ones!. Their pricing strategy sets prices slightly higher than what competitors charge but still affordable enough so customers don’t feel like they’re being overcharged. Distribution mainly takes place through their store located inside Sawgrass Mall but eventually they might consider expanding distribution channels depending on how successful their business becomes over time. Human resources management employs 10 people between full-time employees part-time employees contractors etc… They plan hire additional staff members coming mostly from friends family members within Venezuelan community here Miami – this way not only help create jobs but also build relationships between us those who live around us!. Lastly facilities size capacity currently stands 1 small prepare food location Sawgrass Mall however future plans involve opening 6 more stores next year then 6 per year after until reach desired expansion rate desired number locations across Miami Area..   

By following strategies outlined above Venezuelan Hot Dogs believes it will be able capitalize strengths opportunities available while addressing weaknesses threats facing business thus helping achieve goals objectives set beginning. This should enable them reach 4 million dollars in sales short-term as well open five branches throughout Miami long-term - ultimately making them one most successful companies operating within fast food industry Doral Area!