.

Venezuelan Hot Dogs is a limited liability company founded four years ago by Lucas with five employees. It specializes in gourmet hot dogs and is located in the Doral area of Miami, Florida. The business has been able to survive and grow despite the challenging economic environment and intense competition from other fast food restaurants in the area. This chapter provides an overview of Venezuelan Hot Dogs' current size, legal structure, history, market analysis, product/service description, marketing and sales strategy, human resources policies, operations plan and financial projections for the next three years. 

The company's target market consists of people living in the Doral area who are looking for quality products at competitive prices. Venezuelan Hot Dogs offers two types of hot dog that meet customer needs through taste, convenience, local adaptation and unique recipes served faster than other fast food restaurants. To reach its target market it employs digital campaigns on social media platforms as well as word-of-mouth advertising and fliers distributed in malls. Its pricing strategy is high compared to other fast food restaurants but still competitive enough to attract customers while also ensuring profitability for the business. Distribution is done from a small store located at Sawgrass Mall where all food preparation takes place; plans for expansion include opening six more stores within one year followed by six more stores per year throughout Miami. Human resources policies include benefits for hourly employees as well as employee training plans based on standards set by Venezuelan Hot Dogs . 

Venezuelan Hot Dogs’ financial projections over three years will include income statements , balance sheets , cash flow statements , break even analysis , assumptions used in calculations , sensitivity analysis , capital expenditure budgeting , loan amortization tables and tax planning strategies . This information will enable investors to understand how Venezuelan Hot Dogs plans to achieve its short term objectives while pursuing long term growth opportunities such as expanding into new markets or launching new products/services .