

\section{Operations}\label{sec:operations}
\nonumsubsubsection*{Summary}
This chapter outlines the current size and capacity of Venezuelan Hot Dogs' physical facilities, operational processes, inventory management and supply chain management. It also considers plans for expanding the facilities and hiring additional personnel in the future. 

Venezuelan Hot Dogs is a limited liability company that has been in operation for four years. It currently employs five people and has one small facility to prepare food in Doral, Florida as well as a small store in Sawgrass Mall. The company specializes in selling gourmet hot dogs to meet the demands of its target market - people living in Doral. 

The operational processes involve three suppliers for sausages, one supplier for bread, and all sauces and other ingredients are bought from Costco. Venezuelan Hot Dogs manages its inventory on a weekly basis by analyzing sales data from the week before. In terms of expanding their facilities, they plan to open six more stores within the next year with an additional six stores each year thereafter within Miami area. 

In terms of human resources (HR), Venezuelan Hot Dogs currently employs ten people with plans to hire friends and family from their local community going forward. They operate under basic HR policies such as hourly employees receiving benefits, time off, performance evaluations etc., as stipulated by law. There is also a training plan implemented to ensure staff adhere to company standards when serving customers or preparing food items. 

 Finally, Venezuelan Hot Dogs differentiates itself from competitors through focusing on its target market - the local Venezuelan community - with great packaging and convenience served faster than other fast-food restaurants offering similar products or services