 

Venezuelan Hot Dogs is a business that sells hot dogs gourmet. It was founded four years ago by Lucas in New York City and has since grown to five employees. The target market for Venezuelan Hot Dogs are the people living in the Doral area, and their competitive advantage lies in quality and services. Their short-term goal is to sell 4 million hot dogs, while the long-term goal is to have 5 branches. The main competitors of Venezuelan Hot Dogs are all the food restaurants located in Sawgrass Mall, with a total market size of 30 billion dollars.

The current market demand for products or services offered by Venezuelan Hot Dogs is high due to full malls, while trends within the industry focus on healthier food options such as fast food. Challenges facing this industry include high competition, low prices, and supply chain issues. Sources of competitive pressure come from price competition, product differentiation, and marketing strategies used by competitors such as McDonalds or Wendies. Supplier bargaining power is high due to there being only one bread supplier while buyer bargaining power is low because buyers cannot negotiate prices or terms. Threats of new entrants into this industry are present every day as well as threats from substitutes with new healthy options available to customers instead of traditional fast food items sold at Venezuelan Hot Dogs . 

To meet customer needs, Venezuelan Hot Dogs offers taste along with convenience which sets them apart from competitors allowing them to capitalize on their strengths such as unique recipes while addressing weaknesses such as limited resources through marketing campaigns focused on their target audience -the Venezuelan community located in Doral area-. Strategies implemented also involve reaching out to potential customers through advertising social media campaigns direct sales pricing strategies distribution methods differentiating their products or services from those offered by competitors employee training development plans HR policies workforce expansion physical facility capacity inventory management supply chain management operations processes etc..   Through these strategies Venezuelan Hot Dogs can continue competing against other fast food chains within their industry while capitalizing on opportunities available to them thus meeting short-term long-term business goals successfully making profits providing quality service satisfying customers needs maintaining a strong brand name being part of an ever growing dynamic industry etc..