

\section{Operations}\label{sec:operations}
\nonumsubtitle{Summary.} Venezuelan Hot Dogs is a Limited Liability Company founded 4 years ago, with 5 employees. It offers hot dogs gourmet to the people living in the Doral, with a competitive advantage of quality and services. The main operational processes are manufacturing, fulfillment and customer service. There is 1 small facility to prepare food in Doral and 1 small store in Sawgrass Mall. The plan for managing inventory and supply chain management is to have an small area for frozen food and purchase every week analyzing the sales for that week. 

Venezuelan Hot Dogs has been in operation for 4 years, offering hot dogs gourmet to its target audience of people living in the Doral area. Its competitive advantage lies in its quality products and services which sets it apart from other competitors within the industry. Venezuelan Hot Dogs currently employs 5 members on its management team who oversee operations including Lucas as President, Raul as Vice President, and Andres as Operations Manager. 

The current size of Venezuelan Hot Dogs’ physical facilities consists of one small facility located in Doral used to prepare food items such as sausages, breads and sauces; plus one additional small store located at Sawgrass Mall where customers can purchase their products directly from them. In order to expand their facilities further they plan on opening 6 more stores over the next year within Miami's vicinity followed by 6 more stores per year thereafter until they reach their long term goal of having 5 branches across Miami-Dade County by 2025. 

In terms of operational processes Venezuelan Hot Dogs’ primary focus lies on manufacturing, fulfillment and customer service duties which includes 3 suppliers for sausages; 1 supplier for breads; all sauces & ingredients purchased from Costco; plus an inventory system consisting of an area designated solely towards frozen products with weekly purchases based off sales analyzed during that same week period. They also have plans on implementing a training program designed specifically around their standards so new employees can be properly trained before being assigned any tasks or duties related to production or customer service matters respectively . 

 Lastly when it comes down to human resources matters Venezuelan Hot Dogs currently has 10 full time employees (with plans on hiring friends & family members within Venezuela's community) along side HR policies such as benefits packages , performance evaluations & time off allowances ; all compliant with local regulations found within Florida's state laws .