

\section{Operations}\label{sec:operations} Venezuelan Hot Dogs is owned and operated by Lucas. The business has been in operation for 4 years and consists of 5 employees. Our operations are focused on selling gourmet hot dogs in the Doral area, with a competitive advantage of quality and service. Our short-term goals are to sell 4 million dollars worth of hot dogs, while our long-term goal is to have 5 branches throughout Miami. We operate as a Limited Liability Company. 

Our physical facilities consist of one small preparation area in the Doral area, as well as one small store located in the Sawgrass Mall. We plan to expand our facilities by opening 6 stores during the next year, followed by 6 more stores per year in the Miami area going forward. Our operational processes include sourcing 3 suppliers for sausage, 1 supplier for bread, and purchasing all sauces and other ingredients from Costco. Inventory management is done on a weekly basis according to sales data from previous weeks. 

Our target market is the Venezuelan community living in Doral, which we plan to reach through social media campaigns, digital advertising campaigns, word-of-mouth recommendations, and fliers distributed at malls within our target market radius. Our pricing strategy focuses on offering high prices relative to other fast food restaurants while still providing value for customers through taste and convenience benefits unique to our product offerings – namely local adaptations that cater specifically towards Venezuelans’ tastes. Product distribution takes place at our store location within the Sawgrass Mall where customers can purchase hot dogs directly from us or order them online via delivery services like Uber Eats or Grubhub if they prefer not having to leave their homes or offices for lunch/dinner breaks etc.. Lastly we differentiate ourselves from competitors through strong focus on catering towards Venezuelans’ tastes with unique recipes that cannot be found elsewhere locally; also through great packaging options that make it easier for people who want something quick but don’t want it messy (i.e., no need for extra utensils etc.). 

In terms of human resources management we currently employ 10 people across full-time/part-time positions; however we plan on expanding this number further by hiring friends & family members who already live within Venezuela’s community here in Miami so they can help us better understand what kind of flavors & preferences locals are looking for when it comes down to hot dog recipes etc.. Furthermore we have basic HR policies such as those related with benefits/time off/performance evaluations which comply with standard regulations set forth by law here in Florida – i.e., hourly employees etc.. Lastly employee training & development plans are also implemented so personnel can learn how best run operations according to company standards & expectations (i.e., customer service protocols/product knowledge/etc.). 

 Summary: Venezuelan Hot Dogs has been operating since 4 years ago offering gourmet hotdogs targeting Venezuelans living in Doral Area , competing based