 and the section.

This chapter of Venezuelan Hot Dogs covers the operations of the company, which is a Limited Liability Company that has been in business for four years with five employees managed by Lucas (President), Raul (Vice President) and Andres (Operations Manager). The company has two physical facilities, one small location to prepare food in Doral area and one store located in Sawgrass Mall. The operational processes include manufacturing, fulfillment and customer service. Venezuelan Hot Dogs sources its sausage from three suppliers, bread from one supplier while other ingredients are purchased from Costco. To manage inventory and supply chain management, Venezuelan Hot Dogs dedicates an area for frozen food with weekly purchases based on sales analysis data from previous week. 

In order to reach its target market of Venezuelans living in Doral area, Venezuelan Hot Dogs plans to use social media campaigns, digital campaigns as well as word-of-mouth marketing strategies such as fliers at mall locations. Pricing will be set higher than other fast food restaurants due to their quality product offerings while distribution will occur solely at their store located in Sawgrass Mall. In terms of human resource management, Venezuelan Hot Dogs plans to hire family members or friends within local Venezuelan community while following legal regulations regarding hourly employees such as time off benefits or performance evaluations policies when necessary; training plans have also been developed which focus on standardizing operations across all stores if expansion occurs over time.