

\section{Product or Service Description}\label{sec:product}
\nonumsubsection{Executive Summary} Venezuelan Hot Dogs is a business that sells gourmet hot dogs to the people living in the Doral. Our competitive advantage lies in our quality and service, and our short-term and long-term business goals are to sell 4 million and have 5 branches. 

Summary: Venezuelan Hot Dogs is a business that sells gourmet hot dogs with quality and service as its competitive advantage, aiming to sell 4 million products by having 5 branches. 

\nonumsubsection{Company Description} Venezuelan Hot Dogs is a Limited Liability Company that has been in operation for four years. The key members of the management team are Lucas - President, Raul - Vice President, and Andres - Operations Manager. Currently, there are five employees working for the company with an annual revenue of 30 billion dollars. The company was founded four years ago when Lucas had a small point of hotdogs in New York City which was very successful. 

Summary: Venezuelan Hot Dogs is a Limited Liability Company operating for four years with five employees generating an annual revenue of 30 billion dollars; it was founded when Lucas had a successful small point of hotdogs in New York City. 

 \nonumsubsection{Market Analysis} Our main competitors are all the food restaurants in the Sawgrass Mall, where we operate from; our market size is estimated at 30 billion dollars with high demand all year round due to how full malls usually get throughout the year. The trends within our industry include people looking for healthier food options as well as fast food options; some of the main challenges facing us include high competition, low prices, supply chain issues, bargaining power of suppliers being high due to there being only one bread supplier available and no bargaining power among buyers due to lack thereof. There is also always new entrants coming into our industry every day along with substitutes such as healthier options which pose threats to us too.  
 
 Summary: The main competitors located at Sawgrass Mall have an estimated market size of 30 billion dollars with high demand all year round; trends include people looking for healthier food options as well as fast food options while challenges involve high competition, low prices, supply chain issues etc.; threats posed by new entrants coming into our industry every day along with substitutes such as healthy alternatives exist too .

 \nonumsubsection{Product or Service Description} Venezuelan Hot Dogs offers two types of hot dogs – ‘hot dog 1’ and ‘hot dog 2’ – which meet customer needs through taste, speediness and convenience due to its local adaptation within Venezuela's community; key features/benefits include taste/convenience/local adaptation while internal strengths consist mainly on unique recipes while weaknesses lie on limited capital available. External opportunities involve new markets/partnerships/technological advancements while external threats consist mainly on competition/regulatory changes/