

\section{Product or Service Description}\label{sec:description}
Venezuelan Hot Dogs is a business that offers hot dogs gourmet to the people living in the Doral. They specialize in Venezuelan flavors and offer two types of hot dogs, hot dog 1 and hot dog 2. The business has been operating for four years and is owned by Lucas, who also serves as President. Raul is Vice President and Andres is Operations Manager. There are currently five employees working at Venezuelan Hot Dogs. 

The business was founded when Lucas had a small point of hotdogs in New York City which was very successful. Venezuelan Hot Dogs’ main competitors are all the food restaurants in the Sawgrass Mall, with an estimated market size of 30 billion dollars. The current market demand for their products or services is high due to the full malls, but there is competition from great chains such as McDonalds and Wendies which leads to price competition, product differentiation, marketing pressure and low prices from suppliers. However, there are new healthy options available which creates a threat of substitutes in the industry as well as new entrants every day creating a threat of new entrants into the market. 

Venezuelan Hot Dogs provides two types of hot dogs that meet customer needs through taste, fast service and convenience while setting them apart from competitors with unique recipes adapted to local tastes within their target demographic (the Venezuelan community). Their internal strengths include a strong brand identity built on quality ingredients and services while their weaknesses include limited resources due to lack of capital investment. External opportunities include new markets through partnerships or technological advancements while external threats come from competition, regulatory changes or economic downturns. To capitalize on these strengths and opportunities they plan to implement marketing strategies focusing on the Venezuelan community such as social media campaigns or direct sales with fliers distributed at malls around Doral area where their target demographic resides. 

Their pricing strategy focuses on providing higher prices than other fast food restaurants but still offering competitive prices compared to other gourmet options; distribution will be done exclusively at their store located in Sawgrass mall’s food corner while inventory management will be handled by analyzing weekly sales data stored at their small facility dedicated exclusively for frozen food storage located near Doral area; employee training plans have been implemented following standards set by owners; finally future expansion plans involve opening six more stores over next year throughout Miami area targeting Venezuela community specifically through great packaging design & convenience served faster than traditional fast-food restaurants . 

Summary: Venezuelan Hot Dogs specializes in selling gourmet hot dogs with unique recipes adapted to local tastes within its target demographic - Venezuelans living in Doral Area - competing against other restaurants operating within Sawgrass Mall with estimated market size of 30 billion dollars facing competitive pressures like price competition & product differentiation whilst managing inventory & supply chain management through analysis of weekly sales data stored at frozen facility near Doral Area & implementing employee training plans following standards set by owners & planning future expansions involving 6 more stores over next