 

\section{Marketing and Sales Strategy}\label{sec:marketing}
\nonumsubsection{Executive Summary}\label{subsec:executive}
Venezuelan Hot Dogs is a business focused on selling gourmet hot dogs to the people living in the Doral. Our competitive advantage is our quality and services. We have short-term goals of selling 4 million dollars worth of product, and long-term goals of having 5 branches. 

\nonumsubsection{Target Market}\label{subsec:target}
Our target market is the people living in the Doral area. We will reach them through advertising, social media, direct sales, and fliers in the mall. 

\nonumsubsection{Pricing Strategy}\label{subsec:pricing}
Our pricing strategy will be to set a high price for fast food sector as we offer higher quality than other fast food restaurants. This will help differentiate us from our competitors and ensure that we are profitable. 

\nonumsubsection{Product or Service Description}\label{subsec:product} 
We offer hot dogs with unique recipes that meet customer needs such as taste, convenience, speed, and local adaptation to Venezuelan culture. Our products stand out from those of our competitors due to their taste, convenience, local adaptation to Venezuelan culture, strong brand recognition within the Venezuelan community, and great packaging. Our internal strengths include a unique recipe and strong brand recognition among Venezuelans while our weaknesses include limited resources and lack of capital for expansion opportunities. External threats facing us are competition from other fast food restaurants as well as economic downturns which could lead to decreased demand for our products or services . To capitalize on these strengths and opportunities while addressing weaknesses and threats we plan to implement marketing strategies focusing on the Venezuelan community such as digital campaigns , word-of-mouth marketing ,and fliers in malls . 

 \nonumsubsection {Distribution}\label {subsec :distribution }   The product or service will be distributed through a small store located in Sawgrass Mall . This location allows us to reach customers quickly , conveniently ,and efficiently .  

 \nonumsubsection {Human Resources } \ label { subsec : humanresources }    We currently employ 10 full - time employees who receive benefits such as hourly pay , vacation time off , performance evaluations , etc . In order to expand our workforce we plan on hiring friends & family members from within the Venezuelan community . Training plans have been put into place so that personnel can be trained up to company standards .   

 \ nonumsubsection {Operations } \ label { subsec : operations }     Currently we have 1 small facility used for preparing food located in Doral with 1 small store located at Sawgrass Mall . In order to expand operations we plan on opening 6 more stores within the next year with an additional 6 stores per year after that throughout Miami area