

Venezuelan Hot Dogs is a Limited Liability Company that has been in operation for 4 years. The company is run by President Lucas, Vice President Raul and Operations Manager Andres. Venezuelan Hot Dogs offers two types of hot dogs with the goal of selling 4 million units and establishing 5 branches. The company targets people living in the Doral area and differentiates itself from competitors through its quality and services. Venezuelan Hot Dogs faces competition from all other food restaurants in the Sograss Mall, as well as pressure from suppliers due to limited availability of bread supply. 

The market demand for Venezuelan Hot Dog's products is high, but they must compete against fast food chains such as McDonalds and Wendies to remain competitive. New entrants are entering the market frequently, which increases competition further, while new healthy options provide potential substitutes for their products. To capitalize on strengths/opportunities while addressing weaknesses/threats, strategies can be implemented to focus on marketing/communication campaigns targeting specifically the Venezuelan community. 

The size of Venezuelan Hot Dog's market is estimated at 30 billion dollars with high demand seen across malls nationwide due to convenience-based purchasing decisions made by customers who are looking for innovative tastes (e.g., Venezuelan flavours). Major competitors exist within this industry including fast food chains such as McDonalds or Wendies; however there is also bargaining power from suppliers due to limited availability of bread supply as well as buyers who have no bargaining power when it comes to price competition or product differentiation due to marketing efforts made by larger companies like McDonalds or Wendies dominating this sector . New entrants pose a threat by increasing levels of competition while substitutes also pose a threat due to new healthy options available on the market today 

Venezuelan Hot Dogs offer two types of hot dogs - hot dog 1 and hot dog 2 - that meet customer needs through taste, speed, convenience and local adaptation (Venezuelan community). Unique recipes set these apart from competitors providing an edge over them in terms of taste and quality assurance. Moreover, their target audience consists primarily of Venezuelans living in Doral area thus catering specifically towards their needs making them stand out among other businesses operating within this space.  

Overall it can be concluded that although there exists intense competition within this industry along with external threats such as regulatory changes or economic downturns; if managed properly with targeted strategies focusing on capitalizing on strengths/opportunities while addressing weaknesses/threats then Venezuelan Hot Dogs can achieve success in achieving its goals outlined previously (selling 4 million units & establishing 5 branches).