
Venezuelan Hot Dogs is a Limited Liability Company founded four years ago that provides hot dogs to the people living in the Doral area. It has five employees and an annual revenue of 30 billion dollars, with two types of hot dogs, Hot Dog 1 and Hot Dog 2. The company's competitive advantage lies in its quality and services. Its short-term goal is to sell 4MM and have 5 branches while its long-term goal is to expand into other areas such as Miami. 

Venezuelan Hot Dogs operates out of two physical locations - one used to prepare food located at Calle la colina edificio 32 Av Fuerzas Armadas Caracas, another one located at Sawgrass Mall where products are sold - with plans for further expansion into more stores in the Doral area (6) followed by 6 per year in Miami area. Operational processes involve 3 suppliers for sausages, 1 supplier for breads and all other ingredients being bought from Costco every week based on sales analysis from previous weeks; inventory management also involves having a small space dedicated for frozen foods purchases done weekly according to sales analysis from previous weeks. Human Resources policies include those required by law such as hourly employees benefits, time off policies etc., plus employee training plan designed specifically around Venezuelan Hot Dogs standards which will be implemented through friends or family members within Venezuelan Community when needed due to workforce expansion plans. 

The company's strategy focuses on providing high quality service with competitive prices that can be accessible for everyone in order to attract new customers while keeping existing ones satisfied with their experience. They also use marketing strategies such as social media campaigns on Facebook and Instagram targeting local community members as well as discounts offered during special events like festivals or holidays celebrated within the Venezuelan community living in South Florida. With these strategies they hope to reach their goals of expanding their operations both geographically and financially while maintaining their commitment towards customer satisfaction through excellent services provided by trained personnel who understand the culture of Venezuela and its people’s needs when it comes to food consumption habits.