.s or Wendies. Challenges facing the industry include high competition leading to low prices on certain items making supply chain management difficult while there is also pressure from new entrants every day looking for innovative tastes which can create potential substitutes if not addressed properly. Bargaining power lies mostly with suppliers due to there being only one bread supplier while buyers don't have any bargaining power at all given how much choice they have available on the market today.}
 
\section{Marketing Plan}\label{sec:marketing-plan}
The marketing plan for Venezuelan Hot Dogs is focused on increasing brand awareness, creating customer loyalty and driving sales through promotional activities such as discounts, coupons, and freebies. The company will use digital marketing strategies such as social media campaigns and website optimization to reach its target audience. Additionally, it will implement traditional marketing tactics such as flyers and radio ads to further increase its visibility in the local community. To measure success, Venezuelan Hot Dogs will track customer feedback through surveys and analyze sales data to determine ROI of each campaign. 

\nonumsidenote{The Marketing Plan section outlines Venezuelan Hot Dog's focus on increasing brand awareness, creating customer loyalty and driving sales through promotional activities such as discounts, coupons, and freebies using digital marketing strategies such as social media campaigns and website optimization alongside traditional tactics like flyers and radio ads to further increase visibility in local communities with success tracked by customer feedback surveys and analyzing sales data.}