

\section{Operations}\label{sec:operations}
\nonumsubsection*{Summary} Venezuelan Hot Dogs is a limited liability company that has been in operation for four years. It currently employs five people and has one small facility to prepare food in the Doral area and one small store in the Sawgrass Mall. The operational processes involve three suppliers for the sausage, one supplier for bread and all sauces and other ingredients bought from Costco. Inventory and supply chain management are managed by having a small area for frozen food, with weekly purchases based on sales analysis. 

Venezuelan Hot Dogs offers two hot dog products that meet customer needs of taste, speed, convenience, local adaptation to Venezuelan community, high quality services and great packaging. The key members of its management team are Lucas (President), Raul (Vice President) and Andres (Operations Manager). Its main competitors are all restaurants in the Sawgrass Mall while its main sources of competitive pressure include lower prices, high bargaining power of suppliers due to there being only one bread supplier and no bargaining power from buyers. External threats include economic recession due to competition as well as high competence while internal weaknesses include lack of capital. Strategies have been implemented to capitalize on strengths such as unique recipe while addressing weaknesses like lack of capital through marketing campaigns focused on Venezuelan community. The human resources team currently consists of 10 employees with plans to hire family members from within the Venezuelan community with HR policies following laws related to hourly employees. 

The operations plan includes plans for expanding facilities into six more stores within Doral area annually followed by expansion into Miami area with employee training programs and development plans also in place focusing on standards set by management team. In terms of inventory management, weekly purchases will be made based on sales analysis with differentiation strategies involving focus on Venezuelan Community through great packaging convenience served faster than other fast food restaurants. 

