 

The Alpha Project is a Venezuelan Hot Dogs business that was founded four years ago by Lucas and is currently located at Calle la colina edificio 32 Av Fuerzas Armadas Caracas. The business has a competitive advantage due to its quality and services, with a target market of people living in the Doral. Its short-term and long-term goals are to sell 4 million hot dogs with five branches across the city. To achieve this, the company will need to employ an effective marketing and sales strategy. 

The main competitors for Alpha Project are all food restaurants in the Sograss Mall, with an estimated size of 30 billion dollars for its market. There is high demand for their products or services due to their convenience, taste and local adaptation to Venezuelan communities. The industry faces strong competition from large chains such as McDonalds or Wendies while suppliers have high bargaining power due to limited availability of bread supplies. There is also threat from new entrants entering the market every day as well as substitutes offering healthy options instead. 

To capitalize on these opportunities and address weaknesses/threats, Alpha Project will employ various strategies such as marketing campaigns targeting Venezuelan communities through social media platforms like Facebook, Instagram etc., promotions via discounts/coupons, special offers during holidays/festivals etc., advertising via TV commercials etc., creating loyalty programs for customers & offering delivery services through online orders & mobile applications . They can also collaborate with other businesses like supermarkets/grocery stores who may be willing to stock their products & increase their visibility in public places like malls or airports . Additionally , they should focus on creating innovative recipes which will help them stand out from competitors & differentiate themselves further . 

By employing these strategies , Alpha Project can establish itself firmly within its target market , build customer loyalty & capture more potential customers which would result in increased profits over time . This would ultimately help them reach their short term & long term goals of selling 4 million hot dogs with five branches across the city .