Venezuelan Hot Dogs is a gourmet hot dog company located in Caracas, Venezuela. The company was founded by Lucas with the aim of selling high-quality hot dogs to people living in Doral. Currently, the business has been operating for four years and generates revenue from selling two types of hot dogs - hot dog 1 and hot dog 2. The key members of the management team include Lucas as President, Raul as Vice President, and Andres as Operations Manager.

The main competitors for Venezuelan Hot Dogs are all food restaurants located within Sawgrass Mall. However, there is a huge market opportunity worth $30 billion with high demand for fast food products among mall customers. In terms of industry trends, people are increasingly looking for healthier options when it comes to fast food consumption.

Venezuelan Hot Dogs offers two types of gourmet hotdogs that meet the needs of customers who value taste, convenience and speed. The key features of these products include unique recipe, local adaptation, great packaging and fast service. Despite limited resources, Venezuelan Hot Dogs has been able to create a strong brand identity through its unique recipe.

To capitalize on strengths and opportunities while addressing weaknesses and threats like high competition levels from other players in this sector or economic recessionary pressures; marketing campaigns focused on reaching out to Venezuelan Community could be implemented.

The target market for Venezuelan Hot Dogs is primarily focused on the Venezuelan community living in Doral. The plan to reach this market includes social media advertising campaigns as well as word-of-mouth recommendations from satisfied customers. To differentiate itself from competitors like McDonald's or Wendy's; focus will be placed on serving customers faster than any other restaurant while also offering unique packaging options that appeal specifically towards Venezuelans residing in Doral.

Currently, there are ten employees working at Venezuelan Hot Dogs with plans for expansion into hiring friends and family members within the Venezuelan Community residing in Doral. HR policies currently follow legal requirements with hourly employees being compensated based on law standards. Plans for employee training include developing a training program that aligns with company standards.

Venezuelan Hot Dogs currently operates from two locations - one small facility for food preparation located in Doral and a small store within Sawgrass Mall. Plans for expansion include opening six more stores within Doral over the next year with plans to expand into Miami thereafter. Operational processes include sourcing ingredients from three suppliers for sausage, bread and other sauces while also purchasing additional ingredients from Costco. Inventory management is done on a weekly basis with purchases being made based on sales trends over the past week.

In conclusion, Venezuelan Hot Dogs has a unique selling proposition that appeals to its target market of Venezuelans living in Doral. Despite competition from other fast food restaurants, the company's focus on quality products and services has helped it establish itself as a strong brand in the industry. With plans for expansion into new locations, Venezuelan Hot Dogs is poised for growth in the coming years.