

\section{Product or Service Description}\label{sec:product-service}
\nonumsidenote{Venezuelan Hot Dogs offers gourmet hot dogs with unique Venezuelan recipes, high quality and services, delivered fast and conveniently to the people living in the Doral. The company has been in operation for four years and is managed by Lucas (President), Raul (Vice President) and Andres (Operations Manager). It currently has five employees and sells 4 million annually with plans to open 5 branches. The competitive advantage of Venezuelan Hot Dogs is its unique recipe, taste, convenience, local adaptation and great packaging.} 

Venezuelan Hot Dogs offers two types of hot dogs: hot dog 1 and hot dog 2. These products meet customer needs through their taste, speed of delivery, and convenience. They set themselves apart from competitors by offering a unique recipe that appeals to the local Venezuelan community as well as great packaging and convenience. The key features of these products are their taste, convenience, local adaptation, fast delivery time, quality ingredients used in their preparation process. 

The internal strengths of Venezuelan Hot Dogs include its unique recipe as well as a strong brand built over four years of operations. Its weaknesses include limited resources due to lack of capital investment. External opportunities available to the business include new markets such as the large Venezuelan population in the area who are looking for innovative tastes as well as partnerships with other businesses or technological advancements that could help improve efficiency. External threats facing the business include competition from larger chains such as McDonald's or Wendy's which offer lower prices than Venezuelan Hot Dogs; suppliers who have a high bargaining power; buyers who have no bargaining power; new entrants entering into the market every day; substitutes such as healthy options; economic recession affecting demand for products; regulatory changes that may affect how business is conducted; economic downturns reducing consumer spending power. 

To capitalize on its strengths while addressing weaknesses and threats facing it from external sources, Venezuelan Hot Dogs can implement strategies such as marketing campaigns focused on its target market - Venezuelans living in Doral - through social media channels or digital campaigns along with word-of-mouth advertising via fliers distributed at malls or other public places where potential customers may be found. Pricing strategy should be set at a premium level compared to other fast food restaurants while distribution will take place through sales points located within food corners at Sawgrass Mall itself. In addition to this differentiation strategies should focus on appealing to Venezuelans living in Dora through emphasizing their culture while also providing great packaging options for customers seeking convenience when purchasing goods from them.. 

 For human resources management policies should follow laws regarding hourly employees while also taking into account plans for hiring family members from within Venezuela’s community if possible when expanding workforce size . When it comes to operational processes manufacturing will involve three different suppliers for sausages along with one supplier for bread while sauces can be purchased directly from Costco . Inventory management should involve weekly purchases based on