

Venezuelan Hot Dogs is a new business venture that seeks to provide quality gourmet hot dog services to its customers. The company has been in operation for four years and currently employs five people. It is owned and operated by Lucas, with Raul as vice president and Andres as operations manager. The legal structure of Venezuelan Hot Dogs is a Limited Liability Company (LLC). The main competitors are all the food restaurants in the sograss mall with an estimated market size of 30 billion dollars. There is high demand for Venezuelan Hot Dog's products due to their unique taste and convenience which sets them apart from other fast food restaurants. 

The short-term goal of Venezuelan Hot Dogs is to reach 4 million dollars in sales and open five branches while the long-term goal is to become the go-to destination for Venezuelan hot dogs. To achieve this, they will focus on targeting the Venezuelan community living in the Doral area through social media campaigns, digital advertising campaigns, word-of-mouth referrals, fliers distributed around malls etc., with high prices compared to other fast food restaurants. They plan on hiring friends or family members from within the local community while providing employee training plans based on specific standards set by them. In terms of operations they have one small facility located in Doral used for preparing food while another small store located at Sawgrass Mall serves as their point of sale location with plans for expanding into six more stores within 12 months time frame across Miami area .Inventory management will be handled through weekly purchases based on sales data collected from previous week’s activities . 

The financial table data provided shows a company with consistent revenue of $50,100 each month and cost of goods sold remaining relatively constant at $19,750 per month resulting in a gross profit margin of 60.58%. Operating expenses are $28,095 per month including labor costs ($22,000), rent ($2,500), materials ($500), maintenance ($500) and other costs ($125). After deducting depreciation and amortization (D&A) expenses of $667 per month and interest payments of 0%, the Earnings Before Tax (EBT) is $918 each month. After accounting for current taxes of $184 per month the net income margin is 1.47%. Revenue has grown 80% over five years while expenses have remained relatively stable with inflation at 3%. Total revenue for five years was 13.8 million USD with NIAT being 2 million USD over 5 years; maximum NIAT was 1.1 million USD during that time frame; minimum investment required was 148k USD; NPV@10% was 2.5 million USD; IRR 186%. 

Overall , Venezuela Hot Dogs aims at becoming a leader in providing gourmet hotdogs catering to local communities needs by leveraging internal strengths , capitalizing on external opportunities , addressing weaknesses & threats through effective marketing strategies & operational processes . With consistent growth rate , low