.

Venezuelan Hot Dogs is a newly established business located in Calle la colina edificio 32 Av Fuerzas Armadas Caracas, offering gourmet hot dogs with two different options to its target market of people living in the Doral. Its competitive advantage lies in the quality and services it provides, which sets it apart from other businesses in the area. 

The short-term goal of Venezuelan Hot Dogs is to sell 4 million hot dogs within the first year of operation, while its long-term goal is to expand and have 5 branches by 2025. To achieve these goals, Venezuelan Hot Dogs has implemented several strategies such as providing high quality products and services, creating an online presence through social media platforms, and engaging with customers through promotional activities. In addition, they are also focusing on building relationships with their suppliers to ensure consistent availability of ingredients for their hot dogs. 

In order to create a successful business model for Venezuelan Hot Dogs, Lucas has identified several key elements that should be taken into consideration including pricing strategy, marketing strategy and operational efficiency. He believes that by focusing on these areas he can create a strong foundation for his business which will help him reach his desired goals within the specified timeline. 

Overall, Venezuelan Hot Dogs presents an exciting opportunity for anyone looking to establish a new business venture in the Doral area. With its focus on quality products and services as well as strategic implementation of marketing tactics and operational efficiency practices, this new venture could prove successful if managed correctly over time.