The Marketing and Sales Strategy for Venezuelan Hot Dogs is focused on selling gourmet hot dogs in the Doral area, targeting the local Venezuelan community. The primary objective is to offer new and innovative taste experiences to individuals who are looking for quality ingredients and a unique recipe. The pricing strategy will be higher than other fast food restaurants in the area due to a focus on quality ingredients.

The target market will be reached through social media, digital campaigns, word-of-mouth, and fliers in the mall. The product will be distributed through a sales point located in the food corner of Sawgrass Mall. To differentiate from competitors, focus will be placed on packaging and convenience while serving faster than other fast food restaurants.

Human resources policy includes hourly employees with basic benefits as per law. Friends and family within the Venezuelan community will be hired for workforce expansion.

Plans are in place to expand facilities by opening six more stores within a year followed by six stores per year in Miami. Current operational processes include sourcing three suppliers for sausage, one supplier for bread, and purchasing all sauces and other ingredients from Costco.

To capitalize on strengths such as unique recipe and Venezuelan community presence while addressing weaknesses such as lack of capital, marketing and communication campaigns targeting Venezuelans living in Doral will be implemented. This can help build brand recognition among this specific demographic leading to increased sales volume.

Overall, focusing on quality ingredients combined with excellent customer service catering specifically towards Venezuelans living in Doral can create a successful business model that meets both short-term goals such as selling 4MM hot dogs while also expanding into five branches long-term.