Venezuelan Hot Dogs is a Limited Liability Company that offers two types of gourmet hot dogs made from a unique Venezuelan recipe. The company's target market is the people living in Doral, Florida. Their short-term goal is to sell 4 million hot dogs and have five branches, while their long-term goal is to expand its business to other parts of Miami.

The key features of Venezuelan Hot Dogs' products are their unique recipe, taste, convenience, and local adaptation to the Venezuelan community's preferences. The company's competitive advantage lies in its quality food offerings and exceptional customer service compared to other fast-food restaurants in the area.

One internal strength that sets Venezuelan Hot Dogs apart from competitors is its unique recipe for making gourmet hot dogs. However, one internal weakness that limits growth potential for Venezuelan Hot Dogs is limited resources due to lack of capital investment.

An external opportunity available to Venezuelan Hot Dogs is tapping into new markets like partnerships with malls or technological advancements that increase operational efficiency. External threats facing Venezualian Hot Dog include economic recession, high competition, and regulatory changes.

To capitalize on strengths and opportunities while addressing weaknesses and threats, Venezuelan Hot Dogs plans to focus its marketing and communication campaigns on the Venezuelan community in Doral through social media platforms like Facebook, Instagram, Twitter as well as digital campaigns such as Google Ads or Facebook Ads.

Venezuelan Hot Dogs differentiates itself from competitors by focusing on packaging convenience for customers who want quick service without sacrificing quality taste. Their products are served faster than other fast-food restaurants.

In terms of HR policies, basic labor laws are followed regarding benefits like time off or performance evaluations. Future hiring plans include friends or family members within the Venezuelan community. Employee training programs will be implemented based on company standards.

Venezuelan Hot Dogs currently operates out of two locations - a small facility in Doral for food preparation and a store location in Sawgrass Mall where they employ ten people. They have three suppliers for sausage, one supplier for bread, and purchase sauces and other ingredients from Costco. Inventory management is done weekly based on sales analysis for the week.

Future plans include expanding facilities with six additional stores in the Doral area within the next year and six more stores per year in Miami. Venezuelan Hot Dogs aims to achieve its short-term goal of selling 4 million hot dogs and having five branches while expanding its business to other parts of Miami in the long term.