\section{Operations}\label{sec:operations}

Venezuelan Hot Dogs is a Limited Liability Company that has been in operation for four years. The company's key members of the management team are Lucas, the President; Raul, the Vice President; and Andres, the Operations Manager. Currently, Venezuelan Hot Dogs has five employees and generates an annual revenue of $500,000.

\subsection{Facilities}

The company operates two facilities: one small kitchen to prepare food in Doral and a small store located in Sawgrass Mall. In the future, Venezuelan Hot Dogs plans to open six more stores in the Doral area within a year and expand to Miami with six new stores per year.

\subsection{Operational Processes}

To serve its customers with high-quality hot dogs quickly and efficiently, Venezuelan Hot Dogs sources its sausages from three suppliers and bread from one supplier. All other ingredients are purchased from Costco. The company analyzes weekly sales to manage inventory levels effectively.

\subsection{Inventory Management}

Venezuelan Hot Dogs maintains a small area for frozen food storage at its facility. The purchasing department orders supplies every week based on sales data analysis from the previous week.

\subsection{Human Resources}

Currently employing ten people at both locations combined (full-time employees), Venezuelan Hot Dogs plans to hire friends and family members living within the Venezuelan community as part-time employees for future expansion.

The company follows basic HR policies such as hourly employee wages as per law requirements.

\subsection{Training and Development}

Venezuelan Hot Dogs will provide training programs for all personnel based on their standards to ensure quality control across all locations.

With these operational processes in place, Venezuelan Hot Dogs aims to meet its short-term goal of selling $4 million worth of hot dogs while expanding into five branches within two years. Long-term goals include opening additional branches throughout Florida while maintaining quality service standards that set them apart from competitors.

\subsection{Conclusion}

Venezuelan Hot Dogs' operational processes are designed to ensure quality and convenience for customers while maintaining supply chain efficiency. The company's expansion plans aim to capitalize on the high demand for hot dogs in the Doral area, particularly within the Venezuelan community, through targeted marketing campaigns and word-of-mouth referrals.