
Venezuelan Hot Dogs is a limited liability company that has been in operation for four years. It offers two types of hot dogs, ‘Hot Dog 1’ and ‘Hot Dog 2’, to the people living in the Doral area. It has five employees and an annual revenue of $30 billion. Its competitive advantage is quality and services, and its short-term and long-term business goals are to sell 4 million hot dogs and have 5 branches respectively. 

The main competitors in Venezuelan Hot Dogs' industry are the big chains such as McDonalds, Wendies etc., with high competition, low prices and supply chain being the main challenges facing it. The bargaining power of suppliers is high as there's only one bread supplier while buyers do not have any bargaining power. There is a threat from new entrants every day due to the market demand being high for its products or services while substitutes pose a threat as well due to new healthy options available. 

Venezuelan Hot Dogs' products meet customer needs through taste, fast service and convenience while it sets itself apart from competitors through its unique recipe catering specifically to Venezuelan local community tastes. Its internal strengths include a strong brand presence while weaknesses include lack of capital resources available. External opportunities come from new markets opening up as well as technological advancements while external threats come from competition, regulatory changes and economic downturns. 

The data indicates that Venezuelan Hot Dogs is financially sound with total revenue of $13.8 million over 5 years with net income after taxes at $2.1 million over the same period reaching a peak of $6.5 million revenue with $1.1 million net income at maximum level indicating strong growth potential for the company . Minimum investment required was relatively low at $148k , NPV@10% was healthy at $2 . 54m IRR was impressive 186 % . Gross profit margin & net income margin were both consistently high suggesting financial health however EBITDA & EBIT margins should be monitored for improvement . Cash flow remains positive throughout all periods reaching peak balance of 17 , 060 million in period 12 . Company should focus on controlling expenses to maintain profitability & cash flow along with looking into ways to reduce operating costs in order to increase profitability . Target market mainly focused on Venezuelan Community in Doral Area which will be reached through advertising , social media campaigns , direct sales etc.. Pricing strategy set at higher price than other fast food restaurants with product distribution taking place at their store located in Sawgrass Mall Human resource policies based on law with current size 10 employees plans for hiring more family members within target demographic group Operations involve 3 suppliers for sausages , 1 supplier bread sauces bought from Costco inventory management done weekly according to sales data gathered during week . In conclusion company aims capitalize on strengths such unique recipes catered towards local community tastes external opportunities such technological advancements by implementing strategies such marketing campaigns targeting specific demographic groups pricing strategies offering higher value than other fast food restaurants human resource policies compliant