.

Venezuelan Hot Dogs is a limited liability company founded by Lucas four years ago with the goal of providing tasty and convenient food options to the Venezuelan community in Doral, Florida. The business offers two types of hot dogs, Hot Dog 1 and Hot Dog 2, with a focus on quality and services that sets it apart from other fast food restaurants. Currently, Venezuelan Hot Dogs has five employees and an annual revenue of thirty billion dollars. The short-term goal for the company is to sell four million hot dogs while its long-term goal is to have five branches around Miami area. 

The market for Venezuelan Hot Dogs consists primarily of Venezuelans living in Doral who are looking for tasty and convenient food options. There are many competitors in this industry such as McDonalds and Wendies; however, Venezuelan Hot Dogs has an unique recipe that sets it apart from them. The bargaining power of suppliers is high due to only one bread supplier available while there's no bargaining power for buyers since they can't negotiate prices or terms with vendors. New entrants pose a threat to existing businesses as more competition enters the market every day; however, new healthy options also present an opportunity for growth as customers become increasingly health conscious. 

The products offered by Venezuelan Hot Dogs meet customer needs through taste, convenience and local adaptation. Key features include taste, convenience and catering to the local community’s needs; while benefits include faster service than other fast food restaurants as well as unique recipes tailored to Venezuelans’ tastes. Internal strengths include a unique recipe; however weaknesses include lack of capital which can be addressed through marketing campaigns targeting Venezuelans living in Doral specifically. 

Venezuelan Hot Dog’s target market consists solely of Venezuelans living in Doral reachable through social media campaigns, digital advertising and word-of-mouth marketing strategies among others. Pricing strategy focuses on being higher than most fast food restaurants due to their superior quality product; while distribution will take place at their store located inside Sawgrass Mall initially before branching out into other locations around Miami later on down the line if successful enough . Human resources currently consist of 10 employees with plans to hire more family members from within Venezuela’s community . Current operational processes involve 3 suppliers for sausages , 1 supplier for bread , Costco supplying all sauces & ingredients ; inventory & supply chain management handled through weekly analysis & purchases based off sales data . Lastly facilities currently consist of 1 small shop used for preparing foods & 1 small store located inside Sawgrass mall with plans to expand into 6 more stores over next year . 

In conclusion, Venezuelan Hot Dogs provides customers with delicious hot dogs made from traditional recipes that cater specifically towards Venezuelans living in Doral area making it stand out compared to other fast food restaurants nearby offering similar products at lower prices but without any special touches or flavors found only at VHD's establishments.. With proper planning around marketing strategies , pricing models , human resources , operational processes & facilities