.

Venezuelan Hot Dogs is a small business that specializes in Venezuelan cuisine. It currently has 10 employees, including full-time and part-time workers as well as contractors. The company plans to hire friends and family from the Venezuelan community in order to expand its workforce in the future. Venezuelan Hot Dogs follows basic HR policies such as benefits, time off, and performance evaluations for their employees which are based on local laws. They also have an employee training and development plan to train personnel based on their standards which includes customer service, manufacturing, fulfillment, inventory management, supply chain management etc. 

The company believes that investing in its employees is key to success and has implemented various measures to ensure that they are able to perform at their best. Through providing them with benefits such as health insurance and paid time off, the company is able to attract top talent who will be committed for the long term. Additionally, by offering performance evaluations it allows managers to identify areas of improvement for each individual employee so they can continue developing their skillset over time. Finally, through training plans it allows all employees regardless of experience level to learn new skills or further develop existing ones so they can better contribute towards achieving the company’s goals. 

Overall Venezuelan Hot Dogs understands that having a motivated and skilled workforce is essential for any business’s success and is taking steps towards ensuring this by investing in its current team members while also looking into expanding its workforce with individuals from within the Venezuelan community who share similar values as those of the organization itself.