. 

Venezuelan Hot Dogs is a limited liability company that has been in operation for four years, specializing in the sale of gourmet hot dogs to meet the demands of its target market - people living in Doral, Florida. The company currently employs five people and has one small facility to prepare food as well as a small store in Sawgrass Mall. Venezuelan Hot Dogs manages its inventory on a weekly basis by analyzing sales data from the week before and sources three suppliers for sausages, one supplier for bread, and all sauces and other ingredients from Costco. 

In terms of expansion plans, Venezuelan Hot Dogs intends to open six more stores within the next year with an additional six stores each year thereafter within Miami area. To support this growth, they plan to hire friends and family from their local community going forward. They also operate under basic HR policies such as hourly employees receiving benefits, time off, performance evaluations etc., as stipulated by law with a training plan implemented to ensure staff adhere to company standards when serving customers or preparing food items. 

Finally, Venezuelan Hot Dogs differentiates itself from competitors through focusing on its target market - the local Venezuelan community - with great packaging and convenience served faster than other fast-food restaurants offering similar products or services. This strategy allows them to create loyal customers who keep coming back due to their high quality product offerings at competitive prices.