.

Venezuelan Hot Dogs is a small business based in Doral, Florida that specializes in Venezuelan-style hot dogs. The company offers a variety of hot dogs with unique toppings and sauces that are inspired by the flavors of Venezuela. Venezuelan Hot Dogs currently operates with one small facility to prepare food located in Doral, along with a store located at Sawgrass Mall. The company plans to expand its facilities by opening six additional stores within the next year, followed by six more each year afterwards. To manage operations effectively they have three suppliers for their sausages, one supplier for their bread; all sauces and other ingredients are bought from Costco while inventory is managed through weekly purchases based on sales analysis along with an small area dedicated to frozen food storage. They are also working towards developing supply chain management processes that will help ensure quality control over products and materials used throughout production of goods offered at Venezuelan Hot Dogs locations. 

The current size and capacity of physical facilities owned by Venezuelan Hot Dogs consists of one small facility to prepare the food in the Doral area and one small store in the Sawgrass Mall, both which have limited space for production and storage needs. In order to meet customer demand as well as plan for future growth, it is important for Venezuelan Hot Dogs to consider expanding their physical infrastructure if needed. This could include investing into additional equipment or upgrading existing infrastructure so that it can handle increased production levels or larger orders from customers or suppliers when necessary. 

Operational processes utilized by Venezuelan Hot Dogs involve having multiple suppliers for different components such as sausages, breads, sauces and other ingredients; all purchased from Costco while maintaining an small area dedicated solely to frozen food storage needs. Additionally they manage inventory through weekly purchases based on sales analysis which helps them stay up-to-date on what items need replenishing or replacing due to expiration dates being reached or customer demand increasing unexpectedly during certain times of the year. Furthermore they are also working on developing supply chain management processes so that quality control over products and materials used throughout production can be monitored more efficiently ensuring customers receive only top quality goods when ordering from them online or visiting any one of their locations across Miami-Dade county in Florida . 

