

This section of the business plan for Venezuelan Hot Dogs focuses on the human resources aspect of the company. It covers current size and capacity of workforce, hiring plans, HR policies, employee training and development, physical facilities and operational processes. Currently, Venezuelan Hot Dogs has 10 employees consisting of full-time employees, part-time employees and contractors. The company plans to hire more personnel from its Venezuelan community in order to expand its workforce. To ensure that all employees are aware of their rights and responsibilities in the workplace, HR policies have been established for benefits, time off and performance evaluations with a training plan put in place to train personnel based on company standards. The physical facilities consist of one small kitchen located in Doral where food is prepared as well as one smaller store located in Sawgrass Mall where customers can purchase hot dogs with plans to expand by opening six more stores within Doral followed by six more stores per year in Miami area. Operational processes include sourcing ingredients from three suppliers for sausage along with one supplier for bread while sauces and other ingredients are purchased at Costco with inventory managed weekly based on sales data collected over the week while supply chain management is also handled internally. Differentiating itself from competitors Venezuelan Hot Dogs focuses on targeting its Venezuelan community through marketing campaigns such as social media campaigns, digital campaigns, word-of-mouth advertising as well as fliers distributed around Sawgrass Mall with pricing strategy consisting of higher prices compared to other fast food restaurants with product distribution being handled directly at store locations within Sawgrass Mall.