.

Venezuelan Hot Dogs is a Limited Liability Company founded four years ago by Lucas, with the current management team consisting of Lucas as President, Raul as Vice President and Andres as Operations Manager. The company has five employees and is focused on recruiting friends and family from the Venezuelan community to expand its workforce in the future while offering benefits according to law for hourly employees. Training plans are also implemented to train personnel based on company standards. 

The strategy of Venezuelan Hot Dogs is to differentiate itself from competitors through focusing on the Venezuelan Community, great packaging and convenience, served faster than other fast food restaurants. This will be achieved through marketing and communication campaigns targeting this community, social media, digital campaigns, word-of-mouth advertising and fliers in malls. The pricing strategy is set at a high price compared with other fast food restaurants due to its unique recipe and convenience factor. Distribution of products will be done through their store located in the Sawgrass Mall in Doral Area, Miami. 

Inventory management and supply chain management are handled by having a small area for frozen food storage while purchases are made every week based on sales analysis of that week; current operational processes include manufacturing processes such as sausage supplier sourcing (3 suppliers), bread supplier sourcing (1 supplier) while all sauces and other ingredients are bought from Costco; facilities currently consist of one small store located in Sawgrass Mall along with one small facility used for preparing food located in Doral Area; expansion plans include opening 6 more stores within the next year followed by 6 stores per year within Miami area boundaries thereafter . 

Venezuelan Hot Dogs seeks to provide an excellent customer experience by delivering quality products quickly at competitive prices while building relationships with local communities through marketing campaigns targeted at them specifically. Through proper inventory management they can ensure that they have enough stock available when needed while keeping costs low due to weekly sales analysis leading them to purchase only what’s necessary each week. Expansion plans will help increase their reach into new markets allowing them even more opportunities for growth into the future.