 
Venezuelan Hot Dogs is a limited liability company located in Caracas, Venezuela. The business was founded four years ago and has five employees. Venezuelan Hot Dogs offers two types of hot dogs: one regular and one gourmet. The target market for the business is the people living in Doral, Florida, USA. Venezuelan Hot Dogs’ competitive advantage lies in its quality products and services, with short-term goals to sell 4 million units annually and long-term goals to have five branches by 2021. 

The main competitors of Venezuelan Hot Dogs are all food restaurants within the Sawgrass Mall area due to its high demand from customers who look for convenience and taste when eating out at fast food restaurants. The company's revenue is consistent throughout the year, with no other sources of income. Expenses are also consistent, with labor costs accounting for the majority. Gross profit margins remain steady at 60.58%, while EBITDA and EBIT margins are relatively low at 3.16% and 1.83% respectively. Net income margin is also low at 1.47%. The company has a strong cash balance of $17 million at the end of the period as well as increasing total assets and equity year over year indicating that it is in good financial health overall but could benefit from further cost optimization such as reducing packing and shipping costs or increasing sales & marketing efforts to increase revenues further

Overall, Venezuelan Hot Dogs appears to be in a healthy financial position with total revenue of $13 million USD along with maximum revenue of $6 million USD over 5 years resulting in net income after taxes (NIAT) of $2 million USD with maximum NIAT reaching up to $1 million USD - suggesting that there may be potential for improvement through additional revenue sources or reducing expenses while maintaining their competitive advantage through quality products & services offered along with local adaptations specifically targeting Venezuelan communities living in Doral area via unique recipes developed over time through trial-and-error processes conducted by Lucas himself over his four year period running his own business before expanding into larger markets such as Doral trainee . Furthermore minimum investment needed to achieve these results stands at only $148k which brings an NPV@10% value worth around 2$million dollars coupled with IRR values reaching up 186% - making it a viable option for potential investors looking into investing into this sector given its current state & future prospects