Venezuelan Hot Dogs is a company that specializes in providing high-quality hot dogs to customers in a fast and convenient manner. The company currently has one small facility for food preparation in the Doral area and a small store located in the Sawgrass Mall. However, it plans to expand its facilities by opening six more stores in the Doral area within the next year, followed by six stores per year in the Miami area.

The operational processes of Venezuelan Hot Dogs include sourcing sausage from three suppliers, bread from one supplier, and sauces and other ingredients from Costco. The company plans to manage inventory through weekly purchases based on sales analysis for the week. Human resources are an important aspect of operations for Venezuelan Hot Dogs, with ten employees working at the two locations currently. To expand its workforce, the company plans to hire friends and family members from within the Venezuelan community.

Employee training and development is also important for ensuring that all employees meet company standards. A training plan will be implemented to ensure that personnel are trained properly. Marketing and sales strategies will focus on reaching out to the Venezuelan Community in the Doral Area through social media, digital campaigns, word-of-mouth advertising, and fliers at malls.

Venezuelan Hot Dogs' internal strengths include unique recipes while lack of capital remains a weakness which can be addressed through marketing campaigns focused on leveraging opportunities such as innovative tastes desired by people along with targeting huge Venezuelan market looking for these flavors despite external threats like economic recession or high competition pressures.

The product or service will be distributed through sales points located at food corners within malls with a focus on packaging convenience and speedier service than competitors. Pricing strategy will involve charging higher prices compared to other fast-food restaurants due to quality ingredients used.

In conclusion, Venezuelan Hot Dogs aims at expanding its business operations while maintaining quality products/services delivered at faster pace than competitors by ensuring proper inventory and supply chain management, employee training and development, and marketing strategies targeted towards the Venezuelan community.