Venezuelan Hot Dogs is a Limited Liability Company that aims to provide high-quality gourmet hot dogs to the people living in the Doral area. The company offers two different types of hot dogs, which are unique due to their recipe and local adaptation to the Venezuelan community. The key features and benefits of these products are taste, convenience, and quality.

The company has identified some internal strengths such as a unique recipe that sets it apart from competitors. However, it also has some weaknesses such as lack of capital to expand its business further. The external opportunities available for the company include new markets and partnerships with other businesses. On the other hand, economic recession and high competition pose significant threats.

To capitalize on its strengths and opportunities while addressing its weaknesses and threats, Venezuelan Hot Dogs plans on implementing marketing strategies focusing on communication campaigns targeting the Venezuelan community in Doral. It will use social media platforms like Instagram and Facebook along with word-of-mouth advertising techniques to reach out to potential customers.

The pricing strategy of Venezuelan Hot Dogs will be set at a higher price point compared to other fast-food restaurants due to the quality of ingredients used in making its gourmet hot dogs. The company plans on distributing its products through sales points located at food corners in Sawgrass Mall.

To differentiate itself from competitors, Venezuelan Hot Dogs will focus on packaging design that appeals specifically towards Venezuelans' culture while offering faster service than other fast-food restaurants.

As far as human resources are concerned, Venezuelan Hot Dogs currently employs ten personnel consisting of part-time employees who work hourly shifts following standard HR policies regarding time off and performance evaluations. The company plans on expanding its workforce by hiring friends and family members within the Venezuelan community.

Currently, Venezuelan Hot Dogs has two physical locations: one small facility in Doral to prepare food and a small store in Sawgrass Mall. However, it plans on expanding its facilities by opening six more stores in the Doral area within the next year followed by six stores per year in Miami.

In conclusion, Venezuelan Hot Dogs offers gourmet hot dogs with unique flavors that cater specifically towards Venezuelans living in the Doral area. Its competitive advantage is quality products and services that differentiate it from other fast-food restaurants. With proper planning and execution of marketing strategies along with operational efficiency, the company aims to achieve its short-term goal of selling 4MM hot dogs while establishing five branches within the next few years.