\section{Product or Service Description}\label{sec:product}

Venezuelan Hot Dogs is a Limited Liability Company that specializes in selling gourmet hot dogs. The company offers two types of hot dogs, namely hot dog 1 and hot dog 2, which are made from a unique Venezuelan recipe. The target market for the company is the people living in Doral, Florida. 

The competitive advantage of Venezuelan Hot Dogs lies in its quality and services. The short-term goal of the company is to sell 4 million hot dogs and have five branches, while the long-term goal is to expand its business to other parts of Miami.

\subsection{Products or Services Offered}

Venezuelan Hot Dogs offers gourmet hot dogs made from a unique Venezuelan recipe. The company has two types of hot dogs on its menu - hot dog 1 and hot dog 2. These products meet the needs of customers who want taste, convenience, and fast service.

\subsection{Key Features and Benefits}

The key features of Venezuelan Hot Dogs' products are their unique recipe, taste, convenience, and local adaptation to the Venezuelan community's preferences. Customers can enjoy high-quality food with excellent customer service at an affordable price.

\subsection{Competitive Advantage}

The competitive advantage of Venezuelan Hot Dogs lies in its quality food offerings and exceptional customer service compared to other fast-food restaurants in the area.

\subsection{Internal Strengths}

One internal strength that sets Venezuelan Hot Dogs apart from competitors is its unique recipe for making gourmet hot dogs.

\subsection{Internal Weaknesses}

One internal weakness that limits growth potential for Venezuelan Hot Dogs is limited resources due to lack of capital investment.

\subsection{External Opportunities}

An external opportunity available to Venezuelan Hot Dogs is tapping into new markets like partnerships with malls or technological advancements that increase operational efficiency.

\subsection{External Threats}

External threats facing Venezualian Hot Dog include economic recession, high competition, and regulatory changes.

\subsection{Alignment of Internal Strengths and Weaknesses with External Opportunities and Threats}

Venezuelan Hot Dogs' unique recipe for making gourmet hot dogs aligns with the external opportunity of a huge Venezuelan market that wants these flavors. The company's limited resources due to lack of capital investment is a weakness that could limit its ability to capitalize on this opportunity.

\subsection{Strategies}

To capitalize on strengths and opportunities while addressing weaknesses and threats, Venezuelan Hot Dogs plans to focus its marketing and communication campaigns on the Venezuelan community in Doral. This will include social media, digital campaigns, word-of-mouth advertising, fliers in malls, and other targeted strategies.

\section{Marketing and Sales Strategy}\label{sec:marketing}

The target market for Venezuelan Hot Dogs is the Venezuelan community living in the Doral area. The company plans to reach this target market through social media platforms like Facebook, Instagram, Twitter. They also plan to use digital campaigns such as Google Ads or Facebook Ads.

The pricing strategy for their products will be high compared to other fast-food restaurants because they offer gourmet hot dogs made from unique recipes. The product will be distributed through sales points located at food corners in Sawgrass Mall.

Venezuelan Hot Dogs differentiates itself from competitors by focusing on packaging convenience for customers who want quick service without sacrificing quality taste. Their products are served faster than other fast-food restaurants.

\section{Human Resources}\label{sec:hr}

Venezuelan Hot Dogs currently employs ten people - five full-time employees who work at the store location in Sawgrass Mall and five part-time employees who work at their small facility in Doral.
 
In terms of HR policies, basic labor laws are followed regarding benefits like time off or performance evaluations. Future hiring plans include friends or family members within the Venezuelan community. Employee training programs will be implemented based on company standards.

\section{Operations}\label{sec:operations}

Venezuelan Hot Dogs currently operates out of two locations - a small facility in Doral to prepare food and a store location in Sawgrass Mall. They have three suppliers for sausage, one supplier for bread, and purchase sauces and other ingredients from Costco.

Inventory management is done weekly based on sales analysis for the week. Future plans include expanding facilities with six additional stores in the Doral area within the next year and six more stores per year in Miami.