\section{Executive Summary}\label{sec:executive-summary}

Alpha Project is a business that aims to provide high-quality gourmet hot dogs to the people living in Doral. Our products include two types of hot dogs, namely hot dog 1 and hot dog 2, both of which are made with premium ingredients and served with a variety of toppings.

Our target market consists of individuals who appreciate good food and are willing to pay for quality. We believe that there is a significant demand for gourmet hot dogs in Doral, especially among young professionals and families who enjoy trying out new food concepts.

One of our competitive advantages is the quality of our products. We use only the freshest ingredients to ensure that our hot dogs taste delicious every time. Additionally, we offer excellent customer service, ensuring that each customer has an enjoyable dining experience.

Our short-term goal is to sell 4 million hot dogs within the next five years while maintaining consistent quality standards. In the long term, we aim to expand our business by opening five branches across different locations in Florida.

To achieve these goals, we plan on implementing several strategies such as aggressive marketing campaigns through social media platforms like Facebook and Instagram. We will also collaborate with local businesses to promote our brand and attract more customers.

Furthermore, we will invest in staff training programs to ensure that all employees are knowledgeable about our products and can provide exceptional customer service at all times. This will help us build a loyal customer base that will keep coming back for more.

In conclusion, Alpha Project is poised to become one of the leading providers of gourmet hot dogs in Doral by offering high-quality products coupled with excellent services. With proper planning and execution, we believe that we can achieve our short-term sales targets while expanding our business into multiple locations across Florida in the long run.