Venezuelan Hot Dogs is a gourmet hot dog seller that targets the people living in the Doral area. The company offers two types of hot dogs and has a competitive advantage in quality and services. In the short-term, the business aims to sell 4 million hot dogs and have five branches. The market size for Venezuelan Hot Dogs is estimated at $30 billion, with high demand from customers due to the presence of food restaurants in malls. However, there are several challenges facing the industry such as high competition, low prices, and supply chain issues.

The main competitors of Venezuelan Hot Dogs are all food restaurants in Sawgrass Mall. There is a significant threat from new entrants into this market every day, along with considerable threats from substitutes such as healthy options. To capitalize on strengths and opportunities while addressing weaknesses and threats requires marketing communication campaigns focused on reaching out to local communities through social media platforms like Facebook or Instagram ads targeted towards Venezuelans residing within Doral Area who would appreciate these flavors more than others due to their familiarity with them culturally speaking; differentiation strategies focused on packaging design and convenience, faster service than other fast-food restaurants.

Venezuelan Hot Dogs plans to reach its target market through social media, digital campaigns, word-of-mouth recommendations, and fliers in the mall. The pricing strategy is high compared to others in the fast-food sector. The company plans to distribute its products from a sales point in the food corner of Sawgrass Mall.

The current workforce size of Venezuelan Hot Dogs includes ten employees whose HR policies are currently based on hourly wages with no additional benefits or time off policies. Employee training and development programs are available to ensure that personnel meet company standards for quality and services.

Venezuelan Hot Dogs currently has two small facilities - one for preparing food in Doral and another at Sawgrass Mall - but has plans for expansion with six more stores planned for opening within a year followed by six more stores every year after that throughout Miami's metropolitan area. Inventory management is essential as frozen foods have a limited shelf life; therefore, purchases are made weekly based on analyzing weekly sales trends while keeping an adequate supply of ingredients on hand at all times.

In conclusion, Venezuelan Hot Dogs has a unique recipe and offers fast service and convenience compared to other fast-food restaurants in the area. However, there are challenges facing the industry such as high competition, low prices, and supply chain issues. To capitalize on strengths and opportunities while addressing weaknesses and threats requires marketing communication campaigns focused on reaching out to local communities through social media platforms like Facebook or Instagram ads targeted towards Venezuelans residing within Doral Area who would appreciate these flavors more than others due to their familiarity with them culturally speaking; differentiation strategies focused on packaging design and convenience, faster service than other fast-food restaurants. The company plans to expand its business by opening new branches in Doral Area followed by Miami's metropolitan area every year.