 

Venezuelan Hot Dogs is a business founded by Lucas that offers gourmet hot dogs to the people living in the Doral. It has five employees and an annual revenue of 30 billion dollars. Venezuelan Hot Dogs has a unique recipe, strong brand recognition amongst Venezuelans living in Doral Area, and competitive advantage due to its quality and services. The short-term goal of the company is to sell 4 million hot dogs, while its long-term goal is to have 5 branches. 

The main competitors of Venezuelan Hot Dogs are all the food restaurants in the Sawgrass Mall, while its market demand remains high due to full malls. Trends within the industry suggest that people eat healthy food and fast food. Suppliers have high bargaining power due to there being only one bread supplier, while buyers have no bargaining power due to there being no substitutes for Venezuelan Hot Dogs’ products or services. There is a constant threat of new entrants into the market; however, Venezuelan Hot Dogs’ unique recipe sets it apart from competitors which helps capitalize on opportunities available from within its target market (the Venezuelan Community). In terms of pricing strategies, Venezuelan Hot Dog’s prices remain high for fast food sector standards; however, this price reflects their commitment to quality ingredients and customer service as well as their focus on convenience for customers with busy lifestyles. Products are distributed through their store located at Sawgrass Mall where they also differentiate themselves from competitors by focusing heavily on packaging convenience and local adaptation for their primary target market - Venezuelans living in Doral Area - through marketing campaigns that create brand loyalty among customers who appreciate these added benefits when ordering their products or services online or directly at their store location. 

To ensure success going forward, Alpha Project must continue managing finances effectively over time resulting in steady increases in both Operating Cash Flows and respective Net Cashes while avoiding taking on any debt obligations along the way allowing them to retain all profits within the business itself enabling them greater flexibility when considering future investments going forward if necessary. Additionally marketing campaigns should be implemented specifically targeting Venezuela Community via Social Media platforms such as Instagram & Facebook along with Digital Campaigns & Word-of-Mouth advertising methods like fliers distributed throughout mall locations near current store location in order create brand loyalty amongst target demographic thus increasing sales figures over time leading towards company's ultimate long-term goals set forth initially upon creation 4 years ago when business first began operations .