. 

Venezuelan Hot Dogs is a business established by Lucas to provide gourmet hot dogs to the people living in Doral. The company's goal is to sell 4 million hot dogs and have 5 branches in operation within the next year. To reach its target market, Venezuelan Hot Dogs will use a combination of social media campaigns, digital campaigns, word-of-mouth advertising, and fliers distributed in malls. The pricing strategy will be set at a higher level than other fast food restaurants but still relatively affordable for customers. Distribution channels include selling directly from their own store located in Sawgrass Mall as well as through other retail outlets such as supermarkets or convenience stores. To differentiate itself from competitors', Venezuelan Hot Dogs will focus on providing unique recipes that are tailored to local tastes as well as convenience for customers. Additionally, they plan to hire friends and family within the local Venezuelan community who can help spread awareness about their products through word-of-mouth marketing while also providing an understanding of local tastes when it comes to developing new recipes or improving existing ones. Training plans will also be implemented in order to ensure that employees are up-to-date on standards within the business while simultaneously helping them develop further skills that can benefit both themselves personally as well expanding upon what they can do professionally within the company. Finally, operations processes include sourcing ingredients from three different suppliers (sausage supplier plus one bread supplier) plus buying additional ingredients like sauces from Costco along with managing inventory via weekly analysis based on sales data over time so that stock levels remain appropriate given current demand levels at any given time period without having too much excess inventory sitting around needlessly tying up capital unnecessarily