Venezuelan Hot Dogs is a Limited Liability Company that has been in operation for four years, generating an annual revenue of $500,000. The company operates two facilities: one small kitchen to prepare food in Doral and a small store located in Sawgrass Mall. Venezuelan Hot Dogs sources its sausages from three suppliers and bread from one supplier to serve high-quality hot dogs quickly and efficiently. All other ingredients are purchased from Costco, and the company analyzes weekly sales to manage inventory levels effectively.

Venezuelan Hot Dogs maintains a small area for frozen food storage at its facility, and the purchasing department orders supplies every week based on sales data analysis from the previous week. Currently employing ten people at both locations combined (full-time employees), Venezuelan Hot Dogs plans to hire friends and family members living within the Venezuelan community as part-time employees for future expansion.

The company follows basic HR policies such as hourly employee wages as per law requirements. Venezuelan Hot Dogs will provide training programs for all personnel based on their standards to ensure quality control across all locations.

In the future, Venezuelan Hot Dogs plans to open six more stores in the Doral area within a year and expand to Miami with six new stores per year. With these operational processes in place, Venezuelan Hot Dogs aims to meet its short-term goal of selling $4 million worth of hot dogs while expanding into five branches within two years.

Long-term goals include opening additional branches throughout Florida while maintaining quality service standards that set them apart from competitors. The company's expansion plans aim to capitalize on the high demand for hot dogs in the Doral area, particularly within the Venezuelan community, through targeted marketing campaigns and word-of-mouth referrals.

Overall, Venezuelan Hot Dogs' operational processes are designed to ensure quality and convenience for customers while maintaining supply chain efficiency. The company's management team is focused on strategic expansion plans that take advantage of market opportunities without sacrificing their commitment to providing high-quality hot dogs and excellent customer service.