

\section{Operations} \label{sec:operations}
\nonumsubsection{Current Size and Capacity of Physical Facilities} Venezuelan Hot Dogs currently has two physical facilities. The first is a small facility in Doral where the food is prepared, and the second is a small store located in the Sawgrass Mall. \nonumsidenote{Venezuelan Hot Dogs currently has two physical facilities: one for preparation and one for retail.} 

The current size of these facilities are adequate to meet the current demand but there are plans to expand them in the future. The plan is to open six additional stores in the Doral area within the next year, with an additional six stores planned for Miami each year after that. \nonumsidenote{Venezuelan Hot Dogs plans to open six additional stores in Doral within a year, followed by an additional six stores per year for Miami.} 

\nonumsubsection{Operational Processes} Venezuelan Hot Dogs has three suppliers for their sausages, one supplier for their breads, and they purchase all other ingredients from Costco. They have an area dedicated to storing frozen foods and they make weekly purchases based on sales data from the week prior. \nonumsidenote{Venezuelan Hot Dogs has three sausage suppliers, one bread supplier, and buys all other ingredients from Costco; weekly purchases based on sales data.} 

\nonumsubsection{Inventory Management and Supply Chain Management} Venezuelan Hot Dogs utilizes an inventory management system to monitor stock levels of their products at all times. This system allows them to keep track of orders placed by customers as well as any returns or exchanges that need to be processed. Additionally, they use a supply chain management system which helps them manage their relationships with vendors and ensures timely delivery of goods ordered by customers. \nonumsidenote{Venezuelan Hot Dogs uses inventory management system to monitor stock levels; supply chain management system used to manage relationships with vendors.} 

 In order to ensure quality control throughout the entire process, Venezuelan Hot Dogs implements rigorous inspections at every stage of production as well as regular testing of finished products before shipping out orders. This helps ensure customer satisfaction by guaranteeing that only high-quality products reach customers' hands. \nonumsidenote{Rigorous inspections implemented at every stage of production; regular testing done on finished products before shipping out orders.} 

 Finally, Venezuelan Hot Dog's operational processes also include customer service protocols such as handling complaints or providing refunds when necessary. These protocols help ensure customer satisfaction while maintaining positive relationships between customers and employees alike. \nonumsidenote{Customer service protocols include handling complaints or providing refunds when necessary; maintain positive relationships between customers/employees.}

 In summary, Venezuelan Hot Dog's operations involve two physical facilities (one for preparation and one retail), three sausage suppliers (one bread supplier), purchasing all other ingredients from Costco (with weekly purchases based on sales data