.

Venezuelan Hot Dogs is a Limited Liability Company founded by Lucas four years ago with the purpose of offering gourmet hot dogs that meet the needs of their customers in terms of taste, fastness and convenience. Their main products are two types of hot dogs, and their target market is people living in the Doral area. The company has 5 employees and recently moved to Calle la colina edificio 32 Av Fuerzas Armadas Caracas. The key members of the management team include Lucas (President), Raul (Vice President) and Andres (Operations Manager). 

The competitive advantage Venezuelan Hot Dogs has lies in its quality and services, which have enabled them to set short-term goals of selling 4MM products as well as having 5 branches while also setting long-term goals that include expansion into other markets. The main competitors they face are all the food restaurants in Sawgrass Mall, where they must compete with low prices as well as new entrants every day coming into the market for fast food options with healthy options being an increasing threat of substitutes. 

To capitalize on their strengths such as unique recipe or convenience, Venezuelan Hot Dogs plans on implementing marketing strategies targeting Venezuelan community through advertising, social media campaigns, direct sales etc., having a high price strategy for fast food sector and distributing through their own store at Sawgrass Mall as well as word-of-mouth marketing efforts from friends/family within Venezuelan community who will be hired by them in near future due to expansion plans of 6 more stores around Miami area over next year alongside employee training programs based on standards set by them for customer satisfaction purposes. Furthermore, inventory/supply chain management efforts will ensure customer satisfaction along with growth opportunities due to unique product offering coupled with convenient packaging solutions tailored towards local adaptation.