In summary, Venezuelan Hot Dogs is a limited liability company that offers gourmet hot dogs with unique Venezuelan flavors. The target market is the large Venezuelan community in Doral, and the competitive advantage lies in the quality of the products and services provided. The short-term goal is to sell 4 million hot dogs and have five branches within a few years while expanding further into Miami with six new stores per year in the long term.

The market size for fast food in the Doral area is estimated at $30 billion, but there are challenges such as high competition, low prices, and supply chain issues. Major competitors include established chains like McDonald's and Wendy's who pose significant competition due to their lower prices and wider range of menu items.

To capitalize on strengths and opportunities while addressing weaknesses and threats, marketing campaigns should focus on targeting the Venezuelan community through social media platforms like Facebook and Instagram. Pricing strategy will involve setting higher prices than other fast food competitors due to gourmet quality ingredients used in making hot dogs.

The current workforce size is ten employees, but future hiring plans will involve hiring friends and family members from within the Venezuelan community. HR policies include basic legal requirements such as hourly wages, overtime pay, and sick leave.

Operational processes involve sourcing ingredients from three sausage suppliers and one bread supplier while purchasing sauces and other ingredients from Costco. Inventory management involves analyzing sales data weekly to determine inventory levels needed for the following week's production run.