The section on Human Resources in the Venezuelan Hot Dogs company highlights the importance of employees as valuable assets. The current workforce consists of 10 hourly employees, including cooks, cashiers, and a manager. As the company plans to expand by opening more stores in the Doral area and Miami, there is a need to hire more staff members.

The company plans to prioritize hiring from the Venezuelan community as they understand the culture and values better than others. Referrals from existing staff members will also be prioritized when hiring new employees. HR policies are in place that adheres to state laws regarding employee benefits such as minimum wage requirements, overtime pay, and paid sick leave.

Time off requests for vacation or personal reasons should be made at least two weeks before with prior approval from management. Performance evaluations are conducted every six months to identify areas where an employee can improve their skills or performance while providing opportunities for growth within the company.

To maintain consistency in taste across all stores, a training program has been created for new hires on how to prepare hot dogs according to standards. Ongoing training sessions are provided for existing staff members on customer service skills like handling complaints effectively while maintaining a positive attitude towards customers at all times.

In conclusion, having a well-trained and motivated workforce is essential for business success. The Venezuelan Hot Dogs company aims to maintain a positive work environment where everyone feels valued while providing high-quality hot dogs to customers. By prioritizing hiring from the Venezuelan community, following state laws regarding HR policies and investing in employee training and development programs, this goal can be achieved.