

The Alpha Project is a Venezuelan hot dog business founded by Lucas in Caracas. It has been operating for four years and offers two types of hot dogs, Hot Dog 1 and Hot Dog 2. The target market for the business are people living in Doral, as it provides quality and service that stands out from competitors. The short-term goal of the company is to sell 4 million hot dogs and have 5 branches while its long-term goals are to expand into other areas and increase sales. The main competitors are all food restaurants located within Sawgrass Mall, which has an estimated market size of 30 billion dollars. 

Alpha Project's products meet customer needs through taste, speed and convenience while setting them apart from competitors through unique recipes adapted to local communities like Venezuela's own flavors. Their internal strengths include a strong brand name and skilled workforce while weaknesses include lack of capital investment which can be addressed by capitalizing on opportunities like new markets or partnerships as well as external threats such as competition or economic downturns through strategic implementation such as marketing campaigns focused on Venezuelan communities or pricing strategies that differentiate them from competitors. 

Their target market consists mainly of Venezuelans living in Doral area who can be reached through advertising campaigns via social media or direct sales methods such as word-of-mouth or fliers distributed at malls . Pricing strategy for their services will be higher than average fast food establishments but competitively priced against their peers while distribution will take place at designated points within Sawgrass Mall . Employee training plans will also be implemented to ensure that personnel adhere to standards set by Alpha Project while human resource policies like benefits packages ,time off , performance evaluations also need to be taken into consideration when expanding workforce size . Finally physical facilities must also match operational processes such as manufacturing , fulfillment , customer service etcetera so they plan on expanding their current facility size with 6 more stores next year followed by 6 more per year thereafter. 

In conclusion, Alpha Project is a successful Venezuelan hot dog business with ambitious goals for expansion both domestically and abroad. Its success lies in its ability to provide quality products tailored to its customers' needs along with competitive prices and efficient distribution channels. To continue this success, the company must invest in resources such as employee training programs, human resources policies, marketing strategies targeting Venezuelans living in Doral area, physical facilities matching operational processes etcetera along with capital investments needed for expansion plans.