

Venezuelan Hot Dogs is a business that sells gourmet hot dogs to the people living in the Doral area. The company has identified its target market as the Venezuelan community living in this area and plans to reach them through social media, digital campaigns, word-of-mouth, and fliers distributed in malls. Their competitive advantage lies in their quality and services, and their short-term goal is to sell 4 million hot dogs with a long-term goal of having 5 branches. To differentiate themselves from competitors they plan to focus on Venezuelan Community tastes and provide great packaging and convenience served faster than other fast food restaurants. 

The pricing strategy of Venezuelan Hot Dogs is high for fast food sector as they want to provide quality products at an affordable price. The product will be distributed through their sales point located at the food corner of Sawgrass Mall. They currently have 10 employees who are mostly family members or friends from the Venezuelan community with HR policies such as benefits, time off, performance evaluations based on law regulations for hourly employees . They also have training plans for personnel based on their standards . They currently have 1 small facility in Doral to prepare food , 1 small store located at Sawgrass Mall . For inventory management , supply chain management they purchase supplies every week analyzing sales data of past week . In terms of future expansion plans ,they aim to open 6 more stores in next year within Miami area followed by 6 stores per year successively after that . 

All these strategies combined together should help Venezuelan Hot Dogs achieve their goals successfully. With a focus on providing quality products at an affordable price along with marketing campaigns focused on targeting the local community, they can capitalize on their strengths & opportunities while addressing weaknesses & threats posed by external factors like competition & economic downturns.