Venezuelan Hot Dogs is a Limited Liability Company that sells gourmet hot dogs and was founded by Lucas four years ago. The company's headquarters are located at Calle la colina edificio 32 Av Fuerzas Armadas Caracas, and its target market is people living in the Doral area. The short-term goal of Venezuelan Hot Dogs is to sell 4MM hot dogs and have five branches, while its long-term goal is to expand its business across Miami.

In terms of market analysis, all food restaurants in the Sawgrass Mall are considered competitors for Venezuelan Hot Dogs. However, the size of the market for hot dogs in this area alone amounts to 30 billion dollars with high demand from customers. One trend observed in this industry is that people tend to eat healthier food along with fast food.

One major challenge facing this industry includes high competition from other chains like McDonald's and Wendy's who offer lower prices than Venezuelan Hot Dogs. Another challenge includes supply chain management due to limited suppliers for bread and sausage.

Regarding product or service description, Venezuelan Hot Dogs offers two types of hotdogs that meet customer needs through taste, convenience, and speed of delivery compared to its competitors' products or services. Its unique recipe serves as an internal strength; however, lack of capital remains an internal weakness for the company.

Opportunities available externally include a huge Venezuelan market looking for innovative tastes while threats include economic recession and high competition from other chains offering similar products at lower prices.

To capitalize on strengths and opportunities while addressing weaknesses and threats facing their business strategy involves marketing campaigns focused on targeting Venezuelan community members using social media platforms, digital campaigns, and word-of-mouth marketing. The pricing strategy for Venezuelan Hot Dogs is high compared to other fast-food restaurants in the area.

The company plans to distribute its products through sales points located in food corners at Sawgrass Mall. Differentiation from competitors will focus on packaging convenience and faster delivery times.

Venezuelan Hot Dogs currently employs ten employees, with plans to expand the workforce by hiring friends and family members within the Venezuelan community. The company's HR policies align with legal requirements, including hourly wages for employees.

Regarding operations, there are two small facilities: one for preparing food in Doral and another store located in Sawgrass Mall. Plans for expansion include opening six more stores within a year in the Doral area before expanding across Miami.

Current operational processes involve three suppliers for sausage, one supplier for bread, while sauces and ingredients are purchased from Costco. Inventory management involves analyzing weekly sales data to make purchases accordingly.

In conclusion, Venezuelan Hot Dogs aims to provide quality hot dogs that meet customer needs through taste, speed of delivery, and convenience while targeting the Venezuelan community using various marketing strategies. Despite facing challenges such as economic recession and intense competition from other chains offering similar products at lower prices than theirs; their unique recipe serves as an internal strength that helps differentiate them from competitors.