Venezuelan Hot Dogs is a company that aims to offer a unique and authentic taste of Venezuela through its gourmet hot dogs. The marketing and sales strategy for the company will focus on targeting the Venezuelan community in the Doral area, which has limited options available to them in terms of authentic Venezuelan food.

The target market for Venezuelan Hot Dogs is the Venezuelan community living in the Doral area. The company hopes to establish a loyal customer base that will drive repeat business by catering specifically to this market. To reach its target market, Venezuelan Hot Dogs plans to use social media platforms such as Facebook, Instagram, and Twitter to advertise its products. In addition, fliers will be distributed in high-traffic areas such as malls and supermarkets.

Venezuelan Hot Dogs' pricing strategy is aimed at positioning itself as a premium fast-food option while still remaining affordable for customers. The pricing strategy is based on providing quality ingredients that are locally sourced wherever possible while maintaining competitive prices with other fast-food restaurants.

Currently, Venezuelan Hot Dogs operates out of two locations - one small kitchen where food preparation takes place and another small store located within Sawgrass Mall where customers can purchase their hot dogs. Future expansions planned for Miami-Dade County include opening more stores across different locations within each county. The goal is to have five branches within four years while selling 4 million hot dogs annually across all branches combined.

Venezuelan Hot Dogs aims to differentiate itself from competitors by providing a unique and authentic taste of Venezuela through its gourmet hot dogs. The packaging will also be designed to appeal to the Venezuelan community, with images that evoke nostalgia for traditional Venezuelan cuisine.

In terms of human resources, currently ten employees are employed by the company. Basic HR policies are in place in compliance with labor laws, and a training plan has been developed to ensure all personnel are trained according to the company's standards.

Inventory management is done weekly based on sales data analysis for each week. The company has three suppliers for sausages and one supplier for bread while other ingredients are purchased from Costco. Future plans include maintaining inventory management processes similar to current operations.

In conclusion, Venezuelan Hot Dogs is a company that aims to provide a unique and authentic taste of Venezuela through its gourmet hot dogs. The marketing and sales strategy will focus on targeting the Venezuelan community in the Doral area, while the pricing strategy is aimed at positioning itself as a premium fast-food option that remains affordable for customers. Future expansions planned for Miami-Dade County include opening more stores across different locations within each county, while maintaining inventory management processes similar to current operations.