 and the first two sections. 

Venezuelan Hot Dogs is a fast-food business located in Doral, Florida that offers gourmet hot dogs with a unique recipe. Their short-term goal is to sell 4 million units, while their long-term goal is to have five branches. To reach their target market and differentiate themselves from competitors, Venezuelan Hot Dogs plans on implementing a marketing campaign focused on their local Venezuelan community. This will involve utilizing social media, digital campaigns, word-of-mouth marketing, and fliers in malls to promote their product. Their pricing strategy will be slightly higher than other fast food restaurants due to the quality of the product they offer. Distribution will take place through the food corner of Sawgrass Mall. In terms of human resources management, there are currently 10 employees working with Venezuelan Hot Dog but there are plans for hiring more family members within the local community who might have better understanding of flavors natively found in Venezuela which could help improve product offerings even further. Additionally there are HR policies already established such as benefits , time off , performance evaluations etc all following legal guidelines set forth by state laws . Lastly operations wise current facilities consist of one small shop located near Sawgrass mall where production takes place , however there are plans for expanding into 6 more stores within Miami area over next year while managing inventory efficiently through weekly purchases based off sales data collected throughout week . 

In summary Venezuelan Hot Dogs has developed a comprehensive strategy that combines efficient marketing tactics with competitive pricing strategies and an emphasis on customer service to create a successful business model that can stand out amongst competition while also meeting customer expectations regarding taste and convenience at an affordable price point . With its unique recipe as well as targeting its local community specifically it should be able to capitalize on its internal strengths and external opportunities in order to gain competitive advantage over others by providing customers with convenient high quality products at an affordable price point .