


Venezuelan Hot Dogs is a Limited Liability Company that has been in operation for four years. It offers two types of gourmet hot dogs, and its target market is the people living in the Doral. The company has five employees and an annual revenue of 30 billion dollars. Its competitive advantage lies in its quality and services, and its short-term business goals are to sell 4 million dollars worth of hot dogs and establish five branches. Its long-term goal is to become a leader in the Venezuelan fast food industry. 

This business plan provides a comprehensive analysis of Venezuelan Hot Dogs’ financial situation including income statements, balance sheets, cash flow statements, break even points, sensitivity analysis etc. Additionally it also covers details about sources of finance such as debt financing or equity financing. Projected financial statements have been included which provide insight into how much money can be generated from operations over time. Finally all relevant assumptions have been discussed which helps provide an accurate picture of what can be expected from this venture going forward. 

The main competitors are all the food restaurants in the Sawgrass Mall with high competition, low prices, and supply chain issues being some of the challenges facing this industry. The key members of the management team are Lucas (President), Raul (Vice President), and Andres (Operations Manager). The company's products meet customer needs by providing taste, speed, convenience, local adaptation to Venezuelan culture unique recipes strong brand recognition as well as skilled workforce . High price for fast food sector is set as pricing strategy while social media campaigns will be used to reach out to target markets . Human resource policies focus on hourly employees while operational processes involve three suppliers for sausages , one supplier for breads ,and Costco for sauces . An inventory management system will be put into place along with six new stores opening up every year in Miami area . 

The monthly balance sheet provides a detailed overview of Venezuelan Hot Dog’s financial position at any given point with total assets increasing by $735 from November 2020 to December 2020 due mainly to an increase in both current assets ($1402) & fixed assets ($333) respectively . Current Assets increased due to additional investments made into company while inventory levels rose due to higher sales figures during this period . Fixed Assets saw marginal increase due to more money invested into operations during this time frame . Similarly Total Liability + Equity also saw slight increase over same period primarily driven by increases in Trade Payables & Other Payables categories respectively alongside significant earnings growth during December 2020 compared to November 2020 indicating positive performance across all areas within business during these periods . 

In conclusion , Venezuelan Hot Dogs has potential generate significant returns over time given its competitive advantages such as quality service , unique recipes & local adaptation etc along with adequate planning & execution should help achieve short term & long term goals set forth by management team