

\section{Product or Service Description}\label{sec:prodservdes}
\nonumsubsection*{Executive Summary}
Venezuelan Hot Dogs offers gourmet hot dogs to the people living in the Doral area. The company has a competitive advantage of quality and services, and its short-term and long-term business goals are to sell 4 million hot dogs and have 5 branches. 

The legal structure of Venezuelan Hot Dogs is a Limited Liability Company, and it has been in operation for 4 years. The key members of the management team are Lucas (President), Raul (Vice President) and Andres (Operations Manager). The current size of the business is 5 employees with an annual revenue of 30 billion dollars. It was founded by Lucas as a small point of hotdogs in New York City which became very successful. 

The main competitors for Venezuelan Hot Dogs are all the food restaurants in the Sograss Mall, with market demand being high due to all malls being full. Trends in this industry include people eating healthy food and fast food, with major challenges including high competition, low prices and supply chain. Sources of competitive pressure include price competition, product differentiation, marketing, bargaining power from suppliers being high due to only one bread supplier available, bargaining power from buyers being low due to no bargaining power available, threat from new entrants being present every day due to new entrants entering into the market every day as well as threat from substitutes such as new healthy options also present in this industry. 

Venezuelan Hot Dogs offer two types of hot dogs: Hot Dog 1 and Hot Dog 2 which meet customer needs through taste, fast service convenience while setting itself apart from competitors through unique recipes that have been adapted for local communities such as Venezuelans living nearby. Key features/benefits include taste convenience local adaptation while strengths/weaknesses include unique recipes but limited capital respectively. External opportunities include people looking for innovative tastes with huge Venezuelan markets wanting these flavours while external threats include economic recession coupled with high competition. Strategies implemented will involve marketing/communication campaigns focused on Venezuelan communities within target markets reached through advertising social media direct sales etc., pricing strategy involving higher prices than usual fast food sector while products distributed at sales points located within Sawgrass Mall with differentiation achieved by focus on Venezuelan community coupled great packaging/convenience served faster than other fast food restaurants respectively . Human resources involve 10 employees currently planned hiring involving friends/family within Venezuelan community along with HR policies based on laws regarding hourly employees training plans developed based standards set by company itself etc., Operations involve physical facilities sized 1 small used prepare food located Doral along expansion plans 6 more stores next year followed 6 per year Miami area inventory managed weekly analysing sales week supply chain managed 3 suppliers sausage 1 supplier bread sauces ingredients bought Costco respectively .  

In conclusion , Venezuelan Hot Dogs offers gourmet hot dogs tailored towards local communities such as Venezuelans living nearby using unique recipes combined convenience great