\section{Product or Service Description}\label{sec:product}

Venezuelan Hot Dogs is a Limited Liability Company that offers gourmet hot dogs to the people living in the Doral area. Our main goal is to provide high-quality products and services to our customers, which include two different types of hot dogs: hot dog 1 and hot dog 2.

Our products meet the needs of our customers by providing them with a delicious taste, fast service, and convenience. We believe that our unique recipe sets us apart from our competitors. Our key features and benefits are taste, convenience, and local adaptation to the Venezuelan community.

We have identified some internal strengths such as a unique recipe that no one else has in the market. However, we also have some weaknesses such as lack of capital to expand our business further.

The external opportunities available for us are new markets and partnerships with other businesses. The Venezuelan community in the area is looking for innovative tastes, which gives us an excellent opportunity to serve them better. On the other hand, economic recession and high competition pose significant threats to our business.

To capitalize on our strengths and opportunities while addressing our weaknesses and threats, we plan on implementing marketing strategies focusing on communication campaigns targeting the Venezuelan community in Doral. We will use social media platforms like Instagram and Facebook along with word-of-mouth advertising techniques to reach out to potential customers.

Our pricing strategy will be set at a higher price point compared to other fast-food restaurants due to the quality of ingredients used in making our gourmet hot dogs. We plan on distributing our products through sales points located at food corners in Sawgrass Mall.

To differentiate ourselves from competitors, we will focus on packaging design that appeals specifically towards Venezuelans' culture while offering faster service than other fast-food restaurants.

As far as human resources are concerned, we currently employ ten personnel consisting of part-time employees who work hourly shifts following standard HR policies regarding time off and performance evaluations. We plan on expanding our workforce by hiring friends and family members within the Venezuelan community.

Our current operational processes include manufacturing, fulfillment, and customer service. We have three suppliers for sausages, one supplier for bread, and purchase sauces and other ingredients from Costco. Our plans for managing inventory involve analyzing weekly sales data to order supplies based on demand.

Currently, we have two physical locations: one small facility in Doral to prepare food and a small store in Sawgrass Mall. However, we plan on expanding our facilities by opening six more stores in the Doral area within the next year followed by six stores per year in Miami.

In conclusion, Venezuelan Hot Dogs offers gourmet hot dogs with unique flavors that cater specifically towards Venezuelans living in the Doral area. Our competitive advantage is quality products and services that differentiate us from other fast-food restaurants. With proper planning and execution of marketing strategies along with operational efficiency, we aim to achieve our short-term goal of selling 4MM hot dogs while establishing five branches within the next few years.