

\section{Marketing and Sales Strategy}\label{sec:mss}
\nonumsidenote{The marketing and sales strategy of Venezuelan Hot Dogs will focus on the Venezuelan community in the Doral Area. The company plans to reach its target market through social media, digital campaigns, word-of-mouth, and fliers in the mall. The pricing strategy is to offer a higher price than other fast food restaurants, while still providing value for money. Products will be distributed from the store located in Sawgrass Mall. To differentiate itself from competitors, Venezuelan Hot Dogs will focus on its unique recipe and great packaging with convenience that can be served faster than other fast food restaurants. }

Venezuelan Hot Dogs aims to capitalize on its internal strengths (unique recipes) and external opportunities (Venezuelan community) by creating a marketing and sales strategy that emphasizes these features. The company plans to reach its target market through social media, digital campaigns, word-of-mouth advertising, and fliers in the mall. Additionally, they plan to use their unique recipe as an advantage over competitors by emphasizing it through their promotional activities. 

The pricing strategy of Venezuelan Hot Dogs is designed to be competitive with other fast food restaurants while still providing customers with value for money. By offering high quality products at a reasonable price point they are able to attract customers away from competitors who offer lower quality products at similar prices or higher quality products at much higher prices. 

Products offered by Venezuelan Hot Dogs will be distributed from the store located in Sawgrass Mall which allows them access to a large customer base who may not otherwise have access to their product line due to distance or lack of transportation options available in their area. Additionally, this location provides easy access for customers who wish to purchase items directly from the store itself rather than relying solely upon delivery services or online ordering options available elsewhere within Miami-Dade County or beyond. 

 In order to differentiate themselves further from competitors Venezuelan Hot Dogs has implemented strategies that emphasize their unique recipe as well as great packaging with convenience that can be served faster than other fast food restaurants found within Miami-Dade County or beyond.. This helps them stand out amongst competition while also providing customers with an enjoyable experience when purchasing goods from their establishment which may lead them towards becoming repeat customers over time as well as recommending them amongst friends or family members looking for similar establishments within the area .  

 Finally , Venezuelans Hot Dog’s human resources policies are based upon current labor laws governing hourly employees working within Miami-Dade County . They have also implemented plans for employee training and development which help ensure all personnel are trained accordingto company standards . Additionally , they have begun hiring friends and family members living within local communities such as Doral so as aid local employment levels whilst also ensuring all personnel hired possess adequate knowledge concerning both operations associated with running a successful business suchas theirs as wellas any cultural nuances associated with catering towards specific demographics suchas those found