.

Venezuelan Hot Dogs is a Limited Liability Company founded by Lucas four years ago in Doral, Florida. The company offers gourmet hot dogs to the local community and has seen success due to its competitive advantage of quality and services. Their short-term goal is to sell 4 million hot dogs and have 5 branches, while their long-term plan is to expand further into other markets. They are currently staffed with five employees and have an annual revenue of 30 billion dollars. Venezuelan Hot Dogs competes with all food restaurants in the Sawgrass Mall, which present a challenge due to low prices and supply chain issues. Despite this, there is still a high demand for their products or services; however trends towards healthy food options could prove difficult if not addressed properly. 

Venezuelan Hot Dogs offer two types of hot dog: one and two; both meeting customer needs through taste, fast service and convenience whilst setting them apart from competitors through unique recipes with local adaptations catering to the Venezuelan community nearby. Internal strengths include having a strong brand presence within this community whilst weaknesses include limited resources such as capital investment needed for expansion plans outlined by management team members such as Raul (Vice President). To capitalize on these internal/external strengths/opportunities/weaknesses/threats strategies will be implemented such as marketing campaigns focused on the Venezuelan Community combined with pricing strategies set at higher than average rates for fast food sector standards but still lower than competitors – allowing customers access to premium products at affordable prices – distributed through sales points located within Sawgrass Mall’s food corner plus employee training plans that ensure staff meet operational requirements set by management team members like Andres (Operations Manager).  

In terms of Human Resources currently there are 10 employees working full time but plans exist to hire friends & family from within Venezuela’s community should capacity require it plus HR policies related to benefits & performance evaluations alongside existing operational processes involving manufacturing & fulfillment alongside customer service procedures designed specifically around this niche target market segmentation strategy adopted by management team members like Lucas (President). Finally regarding physical facilities currently there is one small space used for preparation purposes located in Doral plus one store situated inside Sawgrass Mall but expansion plans exist over next year which involve opening 6 more stores throughout Miami area – increasing total number of outlets from 1 up to 7 over 12 months period. 

Overall, Venezuelan Hot Dogs has been successful so far due its competitive advantage of quality and services; however they must continue addressing challenges posed by market trends towards healthy food options as well as competition from other restaurants in order maintain their current success rate going forward into 2021.