

This chapter outlines the operations of Venezuelan Hot Dogs, a limited liability company that has been in operation for four years. The company currently employs five people and is managed by Lucas (President), Raul (Vice President) and Andres (Operations Manager). It offers two types of hot dogs, “Hot Dog 1” and “Hot Dog 2”, to the people living in Doral, Florida. Venezuelan Hot Dogs aims to sell 4 million hot dogs with 5 branches in the near future. 

The physical facilities consist of one small store located at Sawgrass Mall where it prepares food as well as sells them. The company also plans to expand its facilities by opening six more stores within the next year and six additional stores each year after that. It sources its products from three suppliers for sausage, one supplier for bread, and all other ingredients are purchased from Costco. Inventory is managed on a weekly basis based on sales data analysis. 

Venezuelan Hot Dogs' target market stands at 30 billion dollars with high demand due to full malls all over the area. Trends in the industry include people looking for healthier options instead of fast food which creates pressure on prices while buyers have no bargaining power as there are no alternatives available . New entrants are entering the market every day creating threat of new entrants while substitutes such as healthy options create threat of substitutes . 

For marketing purposes , Venezuelan Hot Dogs targets Venezuelans living around Doral area through social media , digital campaigns , word-of-mouth advertising , fliers distributed in malls etcetera . Pricing strategy adopted by company is set higher than usual fast food restaurants but lower than gourmet restaurants aiming at providing customers with value for money experience . Products will be distributed via small store located at Sawgrass mall ensuring convenience for customers who can pick up their orders quickly without waiting long periods like other fast food restaurants offer . Human resource policies follow basic legal regulations with hourly employees hired mostly from friends or family members belonging to Venezuelans community residing around Doral area . Training programs are also offered periodically so employees can stay up-to-date with standards set by company itself  

In conclusion, this chapter outlines current operations structure followed by plans for expansion along with operational processes used by Venezuelan Hot Dogs such as sourcing products from suppliers; managing inventory; targeting customers through marketing campaigns; setting pricing strategies; hiring staffs; offering training programs etcetera. These strategies aim to capitalize on strengths such as unique recipe while addressing weaknesses such as lack of capital through marketing campaigns focused towards Venezuelan community thus helping it achieve its goal of selling 4 million hot dogs with 5 branches in near future