Venezuelan Hot Dogs is a Limited Liability Company that specializes in selling gourmet hot dogs to the Venezuelan community in the Doral area. The company offers two types of hot dogs, namely hot dog 1 and hot dog 2, which are made with a unique recipe. The business aims to sell four million hot dogs and establish five branches in the short-term while expanding its operations by opening more branches in Miami in the long-term.

The market size for fast food options is estimated at $30 billion with high demand for healthy food options. The main challenges facing the industry include high competition, low prices and supply chain issues. The bargaining power of suppliers is high since there's only one bread supplier available. However, there's no bargaining power for buyers, and substitutes pose a threat due to new healthy options being introduced regularly.

The internal strengths of Venezuelan Hot Dogs include a unique recipe catering specifically to Venezuelan tastes; however lack of capital poses an internal weakness. External opportunities exist due to people looking for innovative taste experiences coupled with a large Venezuelan community present in our target area who crave such flavors; economic recession and high competition pose external threats.

Our marketing plan focuses on social media, digital campaigns, word-of-mouth advertising, and fliers targeting specifically the Venezuelan community. Our pricing strategy is high compared to other fast-food restaurants as we focus on packaging convenience while serving faster than others.

We currently have ten employees with plans for hiring friends and family members from our target community based on basic HR policies that offer hourly wages. Additionally, we plan to train personnel based on our standards.

Our operations involve one small facility located in Doral where we prepare food along with a small store located at Sawgrass Mall. We plan to expand by opening six more stores within Doral within a year followed by six per year in Miami. Inventory management involves analyzing weekly sales data to make purchases accordingly.

In conclusion, Venezuelan Hot Dogs has established itself as a unique business that caters to the Venezuelan community in the Doral area. The company has identified its strengths, weaknesses, opportunities and threats while focusing on providing high-quality products and excellent services. The future looks bright for Venezuelan Hot Dogs as it aims to expand its operations and establish itself as a leading player in the fast-food industry.