

\subsection{Monthly Balance Sheet}\label{sec:title}
\nonumsubnote{Summary: This section provides an analysis of the monthly balance sheet for the Alpha Project. It looks at total assets, current assets, cash, accounts receivable, inventories, fixed assets and liabilities. Additionally it examines total liability plus equity, current liabilities, trade payables, other payables and provisions. Finally it reviews long term debt and total equity as well as earnings and equity shareholders.}
The monthly balance sheet for the Alpha Project is a useful tool to analyze the financial health of the company. The table shows that in month m (year y) total assets were 155 589 USD increasing to 163 668 USD by month 12 (year y). This indicates a steady increase in overall asset value over time. 

Looking at current assets specifically there was an increase from 6 256 USD to 21 668 USD over this period which suggests that short-term liquidity is improving steadily over time. Cash increased from 1 647 USD to 17 060 USD indicating a healthy level of liquid funds available for operations or investments. Accounts receivable were zero throughout this period which may suggest either no sales on credit or efficient collection policies have been implemented by Alpha Project. Inventories remained constant at 4 608 USD throughout this period suggesting that inventory management is being handled effectively with minimal waste or excess stock build up occurring during this period. 

Fixed Assets increased from 149 333 USD to 142 000 USD over this period suggesting capital expenditure has been made on long-term projects such as property improvements or new equipment purchases which will benefit Alpha Projects operations in future years when these investments are fully depreciated and can be used without further cost outlay for many years into the future. 

Total Liability plus Equity was 155 589USD increasing to 163 668USD by month 12 (year y). Current Liabilities were 4 855USD throughout this period while Trade Payables increased from 812USD to 812USD indicating ongoing supplier costs are being managed efficiently with no overdue payments occurring during these months due to insufficient funds available within Alpha Projects bank account(s). Other Payables decreased slightly from 3 925USD down to 3 925USD indicating effective management of expenses incurred by Alpha Project during these months ensuring all bills are paid promptly and not left until later months when they may incur late payment fees or penalties if not settled on time. Provisions also decreased slightly from 118USD down to 118USD suggesting any potential losses have been covered through provisioning rather than incurring actual losses due to bad debts etc., thus protecting Alpha Projects bottom line profits significantly during this time frame under review here today. 
Long Term Debt remains zero throughout these months indicating either no borrowing has taken place or existing loans have been paid off entirely leaving no outstanding loan repayments required during this timeframe reviewed here today. Total Equity increases from 150 734USd up 158 814USd showing a healthy