\nonumsidenote{Summary}
The table shows the monthly profit and loss data for Alpha Project over a year. The company's revenue is constant throughout the year, with all of it coming from product sales. The cost of goods sold is also consistent each month. However, operating expenses vary, with labor costs being the highest expense every month. Net income remains relatively stable throughout the year, and all margins are within reasonable ranges.

Alpha Project's revenue comes solely from product sales, which remain constant at $50,100 per month throughout the year. The cost of goods sold is also constant at $19,750 per month. As a result, gross profit remains unchanged each month at $30,350.

Operating expenses vary every month but total to $28,095 each time. Labor costs are consistently the highest expense item at $22,000 per month followed by rent at $2,500 per month and material and maintenance costs both at $500 per month. Other expenses such as IT support ($300), Sales and Marketing ($1,500), and lease fees ($670) make up the remaining operating expenses.

EBITDA (Earnings Before Interest Taxes Depreciation Amortization) measures Alpha Project's profitability before accounting for non-cash depreciation or amortization charges and interest payments on debts. EBITDA remains consistent throughout the year at $1,585 per month while EBIT (Earnings Before Interest Taxes) stands at $918 every period since there are no interest payments made during this time.

Net income stays relatively stable over 12 months with a monthly average of $734 after accounting for taxes paid to government authorities on taxable profits earned by Alpha Project in that fiscal period.

Finally, all margins calculated based on net income show reasonable results considering industry standards; Gross Profit Margin stands around 60%, EBITDA Margin around 3%, EBIT Margin around 2%, and Net Income Margin around 1.5%.