

\subsection{Monthly Balance Sheet}\label{sec:title}
\nonumsidenote{Summary: This section provides an analysis of the monthly balance sheet data for Alpha Project, including total assets, current assets, cash, accounts receivable (A/R), inventories, fixed assets, liabilities and equity. The analysis reveals that the company has been steadily increasing its total asset value over the past year while also maintaining a healthy level of current liabilities and equity.}

The table provided is a monthly balance sheet for Alpha Project. This table includes information on total assets, current assets, cash, accounts receivable (A/R), inventories, fixed assets, liabilities and equity. 

Beginning with total assets in row 1 of the table it can be seen that from month 0 to month 12 there was an increase in total asset value from 155 589 to 163 668. This indicates that Alpha Project has been able to steadily grow its asset base over the past year. 

Looking at current assets in row 2 it can be seen that there was an increase in this category from 6 256 to 21 668 between months 0 and 12 respectively. This is likely due to increased sales as well as new investments by Alpha Project over this time period which have allowed them to acquire more tangible and intangible resources such as cash or inventory items. 

Cash is detailed in row 3 of the table and shows an increase from 1 647 to 17 060 between months 0 and 12 respectively. This suggests that Alpha Project has had a steady influx of money over this time period which could be sourced through either sales or other investments made by the company during this time frame. 
It should also be noted that A/R remains at zero throughout all twelve months indicating that no debts are owed by customers during this period which is beneficial for Alpha Projects financial stability going forward. 

 Inventories are listed in row 5 with values staying constant at 4 608 throughout all twelve months indicating a consistent level of stock being held by Alpha Projects throughout this period which could suggest they have maintained their production levels or alternatively have not experienced any major changes in demand for their products or services during these twelve months.  

 Fixed Assets are detailed in row 6 with values decreasing slightly from 149 333 to 142 000 between months 0 and 12 respectively indicating some sale or depreciation of fixed asset items owned by Alpha Projects during this time frame however overall still remaining relatively stable when compared against other categories such as Cash or Total Assets where larger increases were observed suggesting these changes were minor when compared against other areas within their business operations.  

 Liabilities are listed next with no values present indicating no outstanding debts owed by Alpha Projects during these twelve-month periods however Total Liability + Equity does show increases from 155 589 up until 163 668 between month 0 -12 suggesting some form of debt may have been taken out but without any specific details being given it is difficult to determine what type debt may have