

\subsection{Monthly Balance Sheet \label{sec:title}}
\nonumsidenote{The Monthly Balance Sheet for Alpha Project shows that there is a steady increase in assets, liabilities, and equity from month to month. The total assets increased from 155,589 to 163,668 over the course of the year. Current Assets increased from 6,256 to 21,668 while cash increased from 1,647 to 17,060. Inventories remained constant at 4608 throughout the year. Fixed Assets decreased slightly over the year but still remain high at 142,000. Liabilities and Equity also saw an increase over the course of the year with Total Liability + Equity increasing from 155,589 to 163,668 and Total Equity increasing from 150734 to 158814. Earnings also saw an increase over time with a jump from 734 to 8814.}

The Monthly Balance Sheet for Alpha Project provides insights into how the company is performing financially on a monthly basis. It shows that there is a steady increase in assets as well as liabilities and equity over time which indicates that Alpha Project is doing well financially overall. This can be seen by looking at both current assets and fixed assets which have seen an increase since last month while inventories remain constant throughout this period indicating consistent sales performance of products or services offered by Alpha Project. 

In terms of liabilities and equity it can be seen that both have increased steadily since last month indicating that Alpha project has been able to meet its financial obligations on time as well as maintain good relationships with its creditors or investors who may have provided capital during this period of growth for Alpha Project. Additionally earnings have also seen an impressive jump in value since last month showing that profits are being generated through operations conducted by Alpha project during this period of growth. 

Overall it appears that Alpha project has been performing very well financially during this period with all indicators pointing towards continued success moving forward if these trends continue into future months or quarters ahead for the company. This information can be used by management when making decisions about investments or projects they wish to pursue in order to ensure profitability and long term success for their business operations moving forward into 2021 and beyond for Alpha project