

\subsection{Yearly Cash Flow}\label{sec:title}
\nonumsidenote{This section provides an analysis of the yearly cash flow for Alpha Project. It examines net income, D\&A, WC, operating cash flow, CAPEX-fbank and CAPEX-fshare to determine the overall financial performance of the company. Finally, it provides a summary of the key findings.} 

Alpha Project's yearly cash flow is presented in Table 1. In year 1 (y1), Alpha Project had a net income of 8,814 and an operating cash flow (OCF) of 55,969. The OCF was driven by net income and partially offset by depreciation and amortization (D\&A) expenses as well as working capital (WC) expenses which totaled 8k and 39k respectively. There were no capital expenditure payments from bank or shareholders in y1 meaning that net cash was equal to -94k. This was further offset by 150k from investments resulting in a total cash balance of 56k at the end of y1. 

In year 2 (y2), Alpha Project increased its net income to 43k while keeping D\&A and WC expenses constant at 8k and 34k respectively resulting in an increase in OCF to 86k. Capital expenditures remained zero for both bank payments/loans and shareholder contributions leading to a negative 94k net cash figure which was offset again by 25K investments resulting in 17K total cash balance at the end of y2. 

Year 3 saw another significant increase in Alpha Projects' performance with a 251K increase in net income accompanied by similar levels for D\&A and WC expenses leading to 328K OCF figure which when combined with zero capital expenditures resulted in a positive 328K net cash figure ending up with 345K total cash balance at the end of y3.  
Years 4-5 followed similar trends with increases across all parameters except for shareholder contributions where there were no payments made towards capital expenditures throughout this period leading to 687K total cash balance at the end of y4 followed by 1M+ total balance at the end of year 5 due mainly due to increased investments totaling 150K during this period . 

Overall, Alpha Projects' financial performance has been quite impressive over these 5 years with substantial increases across all categories indicating strong growth potentials moving forward into future years if current trends are maintained or improved upon further given that there have been no major changes on any fronts such as debt financing or other sources that could potentially cause disruption within their operations or financials should they be utilized going forward into their next phase(s). Nevertheless, it would be wise for management team members involved within this project to continue monitoring all associated risks closely while simultaneously taking advantage opportunities available so as not maximize returns on invested resources while minimizing potential losses wherever possible. 

In Summary: Alpha Projects' yearly financial performance has seen steady improvement over