

\subsection{Yearly Profit and Loss}\label{sec:title}
\nonumsidenote{This section provides a summary of the yearly financial performance of Alpha Project, including total assets, current assets, cash, accounts receivable (A/R), inventories, fixed assets, liabilities, current liabilities, trade payables, other payables, provisions and long-term debt. Additionally it includes the total equity and earnings as well as equity shareholders.}

The table data shows that Alpha Project has experienced steady growth in its total assets over the past five years. In 2020 (year 0) the company had 207.708 million in total assets while in 2025 (year 5) it had 2.573 billion. This is an increase of 1.365 billion or 11%. The majority of this increase can be attributed to a rise in fixed asset investments which increased from 142 million to 284 million over this period. 

Current Assets also saw an increase over this period with 65.708 million increasing to 2.313 billion or 3 times its original value in 2020 (year 0). This was driven by increases in both cash holdings and inventories which rose from 55.969 million and 9.740 respectively to 2198403 and 115076 respectively over this period - representing increases of 3 times for cash holdings and 12 times for inventories respectively between 2020 (year 0) to 2025 (year 5). 

Liabilities also rose steadily alongside assets during this period with 48895 increasing to 329196 or 7 times its original value between year 0 and year 5 respectively - driven largely by increases in both trade payables (379 increasing to 379) and other payables (47103 increasing to 319240). Provisions also increased from 1413 up to 9577 over this time period representing a 6 fold increase between year 0 & year 5 respectively indicating that Alpha Project may have been more cautious about potential risks when making investments during these years compared with earlier periods prior to 2020(Year 0). 

 Total Equity & Earnings also saw significant increases rising from 158814 up to 2244280 – representing an increase of almost 14 times its original value between Year 0 & Year 5 respectively – driven largely by an 8 fold increase in earnings from 8814 up to 2069283 during this same time frame indicating that Alpha Projects profits have significantly increased since 2020(Year0). Equity Shareholders followed suit with 150k increasing up 175k – representing a 17% increase over the same time frame indicating that shareholders have seen returns on their investment due mostly likely due alpha projects’s profits being reinvested back into the business rather than distributed out as dividends or bonuses etc..  

 Overall it appears that Alpha Projects overall financial performance has been strong since 2020(Year0) across all key metrics including Total Assets , Current Assets , Liabilities , Total Equity & Earnings as well as Equity Shareholders - indicating that alpha project has been managed effectively since it’s inception