

\subsection{Monthly Profit and Loss \label{sec:title}}
\nonumsidenote{This section summarizes the company Alpha Project's monthly profit and loss. It covers revenue, product sales, cost of goods sold, gross profit, operating expenses, labor costs, rent, material costs, maintenance costs, other expenses (negative recoveries), IT costs, sales and marketing costs lease fees, EBITDA (Earnings Before Interest Taxes Depreciation and Amortization) EBIT (Earnings Before Interest Taxes), interest payments taxes paid net income and various margins.}

The table provided contains data on the company Alpha Project's monthly performance over a period of twelve months. The first column is labeled 'Month' which indicates the month in which each row of data was recorded. The remaining columns represent each month with numerical values corresponding to that month. 

The second row of data lists total revenue for each month with all twelve months showing a value of 50 100. Product sales also show an identical figure for all twelve months at 50 100. Other services listed in the third row have a value of 0 for every month indicating no services were provided during this period. 

Costs incurred by Alpha Project are listed in rows four through eleven with Cost of Goods Sold being 19 750 for every month followed by Gross Profit at 30 350 per month. Operating Expenses are listed next as 28 095 for each month followed by Labor Costs 22 000 Rent 2500 Material Costs 500 Maintenance Costs 500 Other Expenses 125 IT 300 Sales and Marketing 1500 Lease Fees 670 respectively per month across all twelve months. 
EBITDA or Earnings Before Interest Taxes Depreciation and Amortization is shown as 1 585 per month while EBIT or Earnings Before Interest Taxes is 918 per month followed by Interest Payments 0 across all twelve months then Current Tax 184 Net Income 734 respectively per month across all twelve months. Finally Gross Profit Margin EBITDA Margin EBIT Margin and Net Income Margin are 60 58 3 16 1 83 and 1 47 respectively for all twelve months covered in this table.. 

Overall these figures indicate that Alpha Project has been performing steadily over the past year despite some fluctuations in their operating expenses most likely due to changes in their business operations such as hiring new staff or increasing marketing efforts during certain periods throughout the year. Additionally they have managed to maintain a healthy gross profit margin while keeping their current tax liabilities relatively low indicating good financial management practices employed throughout the year-long period covered in this table..