

\subsection{Monthly Cash Flow of Alpha Project}\label{sec:title}
\nonumsidenote{\textit{This subsection explores the monthly cash flow of Alpha Project. The table data shows that net income, depreciation and amortization (D\&A), working capital (WC) and operating cash flow are all stable throughout the year. Capital expenditure is funded by both bank payment/loan and investment, resulting in a net cash inflow of 1,401 US$ million for each month. The total cash balance increases steadily from 1,647 US$ million to 17,060 US$ million over 12 months.}} 

The table data provides an overview of Alpha Project's monthly cash flow for a year-long period starting from January 2021 to December 2021. It can be seen that Net Income (+), D\&A (+) and WC (-) remain constant at 734 US$ million, 667 US$ million and -246 US$ million respectively throughout the year. This suggests that there are no significant changes in these three parameters during the period studied. 

Operating Cash Flow (OCF) is also fairly stable with 1,401 US$ million per month as it is determined by subtracting WC from Net Income plus D\&A. Capital Expenditure (CAPEX) is funded by both Bank Payment / Loan (=) and Investment (+). CAPEX funding through Bank Payment / Loan (=) remains zero throughout the year while CAPEX funding through Investment (+) has a one-time contribution of 150,000 US$ million in January 2021 only. This results in a Net Cash inflow of 1,401US$million for each month which contributes to an increasing total Cash Balance over time from 1,647US$million in January 2021 to 17,060US$million in December 2021 due to compounding effects. 

Overall it can be concluded that Alpha Project's monthly cash flow appears to be quite healthy with steady income streams from Net Income plus D\&A combined with moderate levels of CAPEX funded mainly through Investment contributions rather than bank loans or other forms of debt financing which would have resulted in higher interest payments over time thus reducing net profits for shareholders or owners of the company .