

\subsection{Monthly Cash Flow}\label{sec:title}
\nonumsidenote{This section provides an analysis of the monthly cash flow for Alpha Project. It looks at net income, depreciation and amortization, working capital, operating cash flow, capital expenditure from bank payments/loans, net cash flows and cash balances.}
The table provided shows the monthly cash flow for the Alpha Project over a period of 12 months. The table includes data on net income (+), depreciation and amortization (+), working capital (-), operating cash flow (OCF), capital expenditure from bank payments/loans (=) and net cash flows (+/-). 

Net income is calculated as the sum of all revenues minus all expenses. In this case, it is constant across all 12 months with a value of 734 mm US$. Depreciation and amortization (D&A) is also constant across all 12 months with a value of 667 mm US$. Working capital (WC) is variable across the 12 months with values ranging from -246 mm US$ to 0mm US$. Operating Cash Flow (OCF) is equal to Net Income plus D&A minus WC across all 12 months with values ranging from 1,401mm US$ to 1,647mm US$. Capital Expenditure from Bank Payment/Loan (=) remains constant at 0mm US$ throughout the 12 month period. Net Cash Flows are equal to OCF plus CF from Investment (+/-). In this case CF from Investment remains positive throughout the period with a value of 150,000mm US$, resulting in Net Cash Flows ranging between -148353mm USD and 170600mm USD. Finally, Cash Balance is equal to Net Cash Flows + Previous Month's Balance which ranges between 1647mm USD and 17060mm USD. 

Overall we can see that Alpha Project has experienced positive growth in its monthly cash balance over this period due to its consistent investment into new projects as well as its management of working capital. This suggests that Alpha Project will be able to continue investing into future projects with confidence that it will have sufficient funds available each month. 

Summary: This section provides an analysis of Alpha Project's monthly cash flow over a period of twelve months showing positive growth in its balance due to consistent investment into new projects combined with effective management of working capital.