

\subsection{Yearly Profit and Loss}\label{sec:title}
\nonumsidenote{This section provides an analysis of the profit and loss statement for the Alpha Project over a five-year period. It shows that revenues, product sales, gross profit, EBITDA margin and net income margin have all increased over time. The cost of goods sold has also increased but at a slower rate than revenues. Operating expenses have risen in line with revenue growth, while labor costs have grown faster than other operating costs.} 

The table data provided is for the Alpha Project's yearly profit and loss statement from mm US$ 0 to 5. It shows that total revenues increased from mm US$ 601,200 in year 0 to mm US$ 6,500,492 in year 5. This increase was driven primarily by product sales which grew from mm US$ 601,200 in year 0 to mm US$ 6,500,492 in year 5 - an increase of 983\%. Other services remained flat throughout this period at zero revenue generated. 

Cost of goods sold (COGS) also experienced growth during this period increasing from mm US$ 237000 in year 0 to mm US$ 2800188 in year 5 - a 1128\% rise. This growth was slightly slower than that experienced by total revenues indicating improved efficiency within the production process as well as potential economies of scale associated with larger production runs. 

Gross profit rose steadily from 364200mmUS$, 675227mmUS$, 1191681mmUS$, 2101035mmUS$, 3700303mmUS$. Growth here was slightly slower than that seen with total revenues due to higher COGS associated with larger production runs. Operating expenses similarly rose steadily albeit at a slightly lower rate than both total revenue and gross profits suggesting improved efficiency within operational processes such as labour costs which grew faster than any other operating expense item listed on the table (489456mmUS$, 635216mmUS$, 942152mmUS$, 1746750).  Rent costs were also significant rising from 30000mnUSto 155000mnUSover this period however they still remained relatively low compared to labour costs and other operating expenses such as material costs (11124mnUSDto 70891mnUSD)maintenance (11124mnUSDto 70891mnUSD),others(neg recoveries)(2787mnsUDto 17758mnsUD), IT(3800mnsUDto 4700mnsUD)and Sales & Marketing(33372mnsUDto 212673 mnUSD).  

 EBITDA margin rose steadily over this five-year period increasing from 3.16\%in Year 0 to 21.85\%in Year 5 whilst EBIT margins rose equally significantlyfrom 1.83\%in Year 0 to 21.73\%in Year 5indicating strong improvements in operational efficiency across all areas