

\subsection{Monthly Balance Sheet}\label{sec:title}
\nonumsidenote{The monthly balance sheet for Alpha Project shows that total assets have increased from 155,589 to 163,668 over the twelve-month period. This increase is driven by current assets such as cash and inventories which have increased from 6,256 to 21,668 and 4,608 to 4,608 respectively. Fixed assets have decreased slightly from 149,333 to 142,000 over the same period. Total liabilities and equity also increased over the twelve-month period with total liability plus equity increasing from 155,589 to 163,668 while total equity has increased from 150,734 to 158,814. Earnings of 734 to 8,814 were also recorded during this period.}

The monthly balance sheet for Alpha Project reveals a number of important insights into the company's financial health. Firstly it is evident that total assets have grown significantly over the twelve-month period suggesting that Alpha Project has been able to successfully acquire new resources in order to expand its operations. This growth in assets is largely driven by increases in current assets such as cash and inventories which grew substantially during this time frame indicating that Alpha Project has been able to generate sufficient revenue streams in order for these items to be replenished or replaced on a regular basis. 

Fixed asset levels however decreased slightly over the same time frame indicating that there may have been some downsizing of operations or investments made towards other areas of business activity such as research and development or marketing campaigns which would not necessarily require large amounts of capital investment upfront but still provide long term returns for Alpha Project. 

Total liabilities and equity also experienced an overall increase during this time frame with both total liability plus equity increasing from 155 589to 163 668 while total Equity grew from 150 734to 158 814duringthetwelve monthperiodsuggestingthatAlphaProjecthasbeenabletocontinuouslygeneratesufficientprofitsandretainsomeoftheseprofitsforlongterminvestmentpurposesratherthansimplydistributingalloftheirprofitstoshareholdersasdividendsorotherwiseattheendofeachfinancialyear.Earningsalsoincreasedfrom734to8814overthetwelvemonthperiodfurtherdemonstratingthattherehavebeensignificantlevelsofprofitgenerationoverthisperiodwhichhascontributedtothetotalassetsgrowthandequityaccumulationexperiencedbyAlphaProjectoverthisperiodoftime. 

Finally it should be noted that although current liabilities such as trade payables and other payables did not change substantially throughout this twelve-month period there was an increase in provisions which suggests that Alpha Project may be taking more risks than usual when conducting their business operations or making investments potentially leading them into more uncertain situations where they will need additional funds available at short notice if things do not go according tot heir plans . Long term debt