

\nonumsidenote{\textbf{Summary:} This chapter presents an analysis of the monthly balance sheet data of Alpha Project. It shows that the total assets increased from 155,589 in month 0 to 163,668 in month 12. The current assets increased by 7,412 during this period and cash increased by 15,413. Inventories remained constant throughout the period. Fixed assets decreased slightly but overall showed a positive trend. Total liabilities and equity also increased over time with current liabilities remaining relatively stable and total equity increasing by 8,014 over the 12 months period due to an increase in earnings of 8,814.}

\textbf{Monthly Balance Sheet for Alpha Project}\\
The following table presents a summary of Alpha Project's monthly balance sheet data from month 0 to month 12 (m = month; y = year). The table shows that the total assets have steadily increased from 155,589 in m0y to 163,668 in m12y. During this same period current assets have also seen a steady increase of 7,412 with cash increasing from 1,647 in m0y to 17,060 in m12y. Inventories have remained constant at 4608 during this entire period while fixed assets saw a slight decrease but still showed an overall positive trend with values ranging between 149333 and 142000 over these twelve months.  \\
The liabilities and equity section also experienced growth over this same period with total liability plus equity increasing from 155 589 in m0y to 163 668 in m12y while current liabilities stayed relatively stable at 4855 throughout the whole year. Total equity grew significantly due to an increase of 8814 earnings which was equal to the amount shareholders had invested initially (150000). \\ 
Overall it can be concluded that Alpha Projects financial situation is improving as all its asset categories are showing positive trends while its liabilities remain stable or even decrease slightly when taking into account fixed asset values which show only minor decreases compared to their initial value when looking at them on a yearly basis instead on a monthly basis as presented here above. These results should be encouraging for potential investors who will be able to see how well managed is Alpha Project's finances are which should make them more likely invest their money into it as they will know their funds are safe and secure when investing into such a well managed company like Alpha Project is proving itself being here above through its balance sheets data analysis presented here above..