

\subsection{Monthly Cash Flow}\label{sec:monthly-cash-flow}
\nonumsidenote{This section provides an analysis of the monthly cash flow for Alpha Project. It examines net income, depreciation and amortization (D\&A), working capital (WC), operating cash flow, capital expenditure from both bank payment/loan and from shareholders, cash flow from investment, and total cash balance.}

The table data provided gives a clear indication of the monthly cash flow for Alpha Project. The first column indicates that all amounts are in millions of US dollars. In terms of net income, there is no change over the twelve months as it remains constant at 734 million US dollars. D\&A also remains consistent with 667 million US dollars each month. Working capital has a negative value (-246 million US dollars) in month 0 but then shows no changes throughout the rest of the year with zero values for each month thereafter. 

Operating cash flow is calculated by adding net income plus D\&A minus WC which results in 1,647 million US dollars for month 0 and 1,401 million US dollars for months 1 through 12. Capital expenditure from bank payment/loan is zero across all months while capital expenditure from shareholders is 150000 million US dollars only in month 0. Cash flow from investment is also only present in month 0 at 150000 million US dollars while all other months show zero values here too. Finally, this leaves us with a total cash balance which starts at 1,647 million US dollar in month 0 and increases to 170600 million US dollar by the end of the year due to operating cash flows exceeding expenditures throughout all months except for month 0 where there was a large outlay due to shareholder investment costs. 

Overall this data suggests that Alpha Project has been able to generate significant positive operating cash flows over its first year despite having some large initial outlays due to shareholder investments during its launch period. This bodes well for future operations as long as these positive trends continue into future years without any major surprises or unforeseen circumstances arising along the way.