

\subsection{Monthly Profit and Loss}\label{sec:title}
\nonumsidenote{This section provides an analysis of the monthly profit and loss data for the Alpha Project. We summarize our findings by noting that, overall, revenues have remained consistent throughout the year while costs have been managed well. This has resulted in a strong gross profit margin as well as healthy EBITDA and EBIT margins. However, net income margins remain relatively low due to high operating expenses.}

The table provided contains data on the Alpha Project's monthly revenue, product sales, other services, cost of goods sold (COGS), gross profit, operating expenses, labor cost, rent, material cost maintenance cost others (neg. recoveries), IT Sales and Marketing Lease Fee EBITDA D&A EBIT Interest EBT Current Tax Net Income Gross Profit Margin EBITDA margin EBIT margin Net income margin from January to December 2020. 

Overall it can be seen that revenue has remained steady throughout the year with a total of 50 100 USD each month. Product sales also follow this trend with no variation over time. Other services are not applicable as they remain at 0 USD across all months indicating that they are not part of operations for the Alpha Project during this period. 

COGS is also consistent at 19 750 USD per month which results in a strong gross profit margin of 60 58%. Operating expenses are somewhat higher at 28 095 USD per month which is largely driven by labor costs 22 000 USD rent 2 500 USD material cost 500 USD maintenance cost 500USD others 125USD IT 300USD Sales and Marketing 1 500USD Lease Fee 670USD resulting in an EBITDA of 1585USD per month or 3 16% and an EBIT of 918USD or 1 83%. Interest payments remain constant at 0 across all months resulting in an Earnings Before Taxes (EBT) figure also equal to 918USD per month. Current tax payments are 184USd resulting in a net income figure 734USd or 1 47% each month respectively. 

 In conclusion it can be seen that overall revenues have remained steady throughout 2020 while costs have been managed well resulting in strong margins such as a 60 58% gross profit margin 3 16 %Ebitda Margin 1 83 %Ebit Margin and 1 47 %Net Income Margin respectively .