

\subsection{Yearly Profit and Loss}\label{sec:title}
\nonumsidenote{Summary: This section provides an analysis of the yearly profit and loss for the Alpha Project. It shows that revenues have increased each year, with product sales making up a large portion of the total revenue. Cost of goods sold has risen each year as well, though at a slower rate than revenue. Gross profits have grown steadily over the years, but operating expenses have also risen significantly. Labor costs make up a majority of these expenses, followed by rent and materials costs. EBITDA margin and net income margins have both decreased slightly from one year to the next.}

The table data provided in this section offers an overview of Alpha Project's yearly profit and loss for five consecutive years (mm US$). Revenues have increased each year from 601,200 mm US$ in Year 1 to 6,500,492 mm US$ in Year 5; this is largely due to product sales which account for all of these revenues except 0 mm US$ in Other Services during all five years. Cost of Goods Sold (COGS) has also risen steadily from 237,000 mm US$ in Year 1 to 2,800,188 mm US$ in Year 5; however this increase is less than that seen in revenues as COGS only makes up 39% of total Revenues compared to 61% Product Sales. 

Gross Profit has grown steadily over the five-year period from 364,200 mm US$ in Year 1 to 3,700,303 mm US$ in Year 5; however Operating Expenses (OPEX) have also risen significantly over the same period from 337143 mm US$ to 2279333 mm US$. Labor Costs make up a majority of OPEX with 264000mmUS$, 489456mmUS$, 635216mmUS$, 942152mmUS$, 1746750mmUS$, respectively for Years 1-5; Rent follows closely behind at 30000mmUS$, 60000mmUS$, 120000mmUS$, 150000mmUS$, 155000mmmUSthen Materials cost 6000mmmUSto 70891mmmmUSover five years respectively. Maintenance cost 6000mmmUSto 70891mmmmUSover five years are equal with Material cost while Others (neg recoveries) 1503mmmUSto 17758mmmmUSover five years are relatively small compared with other costs mentioned above. IT 3600mmmUSto 4700mmmmUSover five years and Sales & Marketing 18000mmmUSto 212673mmmmUsover five years are also present but smaller still than those previously mentioned expenses combined together they make up only 10%of OPEX while Labour Cost alone makes up 70%. 
Lease Fee 8040 m U S 670 m U S 670 m U S 670 m U S 670 m U S over 5years is minimal when compared with other