

\subsection{Monthly Balance Sheet (m-y)}\label{sec:title}

\nonumsidenote{\textbf{Summary}: This monthly balance sheet for the company Alpha Project shows that total assets have increased from 155,589 to 163,668 during the 12 month period. Current assets have also grown significantly over this time frame, increasing from 6,256 to 21,668. Cash has grown from 1,647 to 17,060 and inventories remain unchanged at 4608. Fixed Assets decreased slightly from 149333 to 142000 while liabilities and equity have increased steadily over the same period of time.} 

The data in this table reflects the financial health of the company Alpha Project over a 12-month period. Total Assets have increased steadily from 155,589 at the beginning of the year to 163,668 by its end. This indicates that overall assets are growing and that Alpha Project is in a healthy financial position. 

Current Assets have also seen significant growth over this time frame; increasing from 6,256 at the start of the year to 21,668 by its end. Cash has seen an even more dramatic increase; it has grown substantially from 1,647 in January to 17,060 by December. Inventories remain unchanged throughout this period at 4608 which suggests they are being managed properly and not accumulating unnecessarily or being wasted due to spoilage or theft. 

Fixed Assets decreased slightly during this period; decreasing from 149333 in January down to 142000 by December although it still remains higher than when it began so overall there is still growth here as well indicating continued success for Alpha Project's operations. Liabilities and Equity both saw steady increases throughout this time frame which further supports evidence that Alpha Project is doing well financially since these two elements typically rise together as a business becomes more successful and profitable with additional investments or loans taken out for expansion purposes etcetera. 

Overall these figures suggest that Alpha Project is doing quite well financially as evidenced by their continued growth in total assets as well as current assets such as cash and inventories remaining stable throughout this 12-month period indicating proper management strategies are being employed here too allowing them to maximize their profits while minimizing waste or unnecessary expenditures meaning they can continue on their trajectory towards becoming an even bigger success in future months/years ahead!