

\subsection{Monthly Cash Flow}\label{sec:title}
\nonumsidenote{This section provides an analysis of the monthly cash flow for Alpha Project. The table shows the net income, depreciation and amortization, working capital, operating cash flow, capital expenditure from bank and shareholders payments, cash flows from investment activities, and the resulting net cash balance over a twelve-month period.}

The table data indicates that Alpha Project has a positive net income of $734 in each month. This is followed by a large expense for depreciation and amortization (D&A) of $667 per month. Working capital expenses are relatively small at -$246 per month on average. As a result of these factors, operating cash flow is positive at $1,401 per month on average. 

Capital expenditures are split between bank payments or loans (-$0) and shareholder payments (-$150k). There are no loan payments required during this twelve-month period but shareholders must pay out $150k at the beginning of the period. Cash flows from investments total to +$150k in this same time frame. 

The combination of all these factors results in a negative net cash balance at the start of the period (-$148k), followed by increasing positive numbers as more money comes into play throughout the year ($1.4k - $17k). By the end of this twelve-month period, Alpha Project has accumulated a total net cash balance of $17k due to its successful financial management strategies. 

Overall, it appears that Alpha Project’s financial strategy is effective in producing positive results over time despite some initial costs associated with investments and shareholder payments upfront. It is important to note that these figures are based off one particular set of assumptions; if any factor changes such as D&A or WC expenses then it would affect both operating and net cash balances accordingly for better or worse depending on circumstance.