

\subsection{Yearly Profit and Loss}\label{sec:title}
\nonumsidenote{The following analysis will provide insight into the financial performance of Alpha Project during the past five years. The data provided in the table shows that total assets have increased significantly over the past five years, while current liabilities remain relatively stable. Additionally, equity shareholders’ equity has grown significantly due to increases in earnings. This indicates that Alpha Project is a profitable business and is generating positive cash flow.}

The table provided shows the financial performance of Alpha Project over the past five years. As can be seen from the data, total assets have increased substantially from 207,708 in year 0 to 2,573,479 in year 5. This increase has been primarily driven by growth in current assets which have risen from 65,708 in year 0 to 2,313,479 in year 5. Of these current assets cash has been a major contributor increasing from 55,969 to 2198403 over this period. Inventories have also contributed significantly rising from 97400 to 115076 over this period. 

Fixed Assets have remained relatively stable at between 142k and 284k throughout this period indicating that Alpha Project is not investing heavily into long term investments such as property or equipment but instead focusing on short term investments such as inventories or cash which can be converted quickly into revenue if needed. 

Total Liability + Equity has followed a similar trend as Total Assets increasing steadily each year with a slight dip between years 3 and 4 before returning back up again for year 5 indicating that Alpha Projects' liabilities are being managed effectively and not becoming too large relative to its assets. 
Current Liabilities have remained relatively stable throughout this period ranging between 48k and 92k for each of these years indicating that Alpha Projects' suppliers are being paid on time without any significant delays or defaults occurring which could lead to bad debts or other issues down the line such as supplier disputes etc.. Trade payables (379) Other Payables (47103-319240)and Provisions (1413-9577) all show similar trends with no significant changes occurring during this period suggesting effective management of these areas by Alpha Projects' finance team. 

Finally Long Term Debt remains empty throughout this entire period suggesting either there was no need for external financing or it was funded internally through retained earnings rather than taking out loans etc.. Total Equity has grown significantly during this time frame increasing from 158k to 2244283 due largely to increases in Earnings (8814-2069283). Equity Shareholders’ Equity also grew steadily over this same time frame rising from 150K - 175K showing an increase return on investment for shareholders who invested early on into alpha project when it first started out . 

Overall we can conclude that alpha project is performing well financially having seen steady growth across all areas of its finances including total assets , current liabilities , equity shareholders’ equity as well as earnings