

\subsection{Monthly Cash Flow}\label{sec:title}
\nonumsidenote{The monthly cash flow of Alpha Project is a comprehensive analysis of the company's net income, D\&A, WC, operating cash flow, capital expenditure from both bank and shareholder payments/loans, CF from bank payment/loan, net cash, CF from investment and cash balance over 12 months.}

The table above provides an overview of Alpha Project's monthly cash flow. The data shows that the company's net income remains constant at 734 mm US$ for all twelve months. Additionally, D\&A expenses remain at 667 mm US$ for all twelve months. However, the WC fluctuates between -246 mm US$ in month 0 to 0 mm US$ in months 1-12. This indicates that there is no need for additional funding to cover WC costs in subsequent months. 

The operating cash flow also remains relatively consistent throughout the year at 1,401 mm US$. This figure is calculated by subtracting WC from Net Income and D\&A expenses. Capital expenditure does not change significantly either; it remains at 0 for most months except when 150000 mm US$ was invested in month 6 via shareholder payments/loans. On the other hand, no capital expenditure was made through bank payments or loans during any month as indicated by a CF from Bank Payment/Loan value of 0.00 across all twelve rows of data. 

Net Cash is calculated by subtracting Capital Expenditure (both fbank and fshare) from Operating Cash Flow resulting in a value ranging between -148353 mm US$ to 1401mm US$. This figure changes depending on whether or not Capital Expenditure has been made during a particular month; when no capital expenditure has been made Net Cash will be equal to Operating Cash Flow while when there has been capital expenditure it will be lower than Operating Cash Flow due to additional costs incurred. Finally we have our final column which is Cash Balance which takes into account all previous columns and shows how much money Alpha Project had available after each individual month based on its incoming and outgoing funds throughout the year; this ranges between 1647mm US$ (month 0) up to 17060mmUS$ (month 12). 

In conclusion this table provides us with valuable insight into Alpha Projects financials over 12 consecutive months indicating that overall their finances are stable due to consistent Net Income and D\&A expenses as well as minimal fluctuations in their operating costs such as WC and Capital Expenditure resulting in a steady increase in their total available funds (Cash Balance).