 

\subsection{Monthly Cash Flow Forecast \label{sec:title}}
\nonumsidenote{This section provides a detailed analysis of the monthly cash flow forecast for the Alpha Project. The table below shows the net income, depreciation and amortization (D&A), working capital (WC) changes, operating cash flow, capital expenditure from bank payments/loans, net cash, and cash balance for each month of the year.} 

The table above displays data regarding Alpha Project's monthly cash flow. It can be seen that in Month 0 (m0) Net Income is 734 mm US$, D&A is 667 mm US$, WC is -246 mm US$ resulting in an Operating Cash Flow of 1,647 mm US$. Capital Expenditure from Bank Payment/Loan is 0.00 mm US$ and Net Cash is -148353 mm US$. Finally, Cash Balance at m0 is 1,647mm US$. 

The following months reflect similar trends with regard to Net Income and D&A. However it can be observed that WC returns to 0 by m1 and remains constant until m12. This suggests that there are no major changes in inventory or accounts receivable/payable during this period which could have caused a fluctuation in WC figures.  Operating Cash Flow also remains constant throughout except for a one-time injection of 150k from investment at m9 which increases the figure to 14258mmUS$. Lastly, Capital Expenditure from Bank Payment/Loan remains zero throughout as expected due to no loan being taken out during this period.  

Overall it can be concluded that Alpha Project has a steady operating performance with no major fluctuations in its financials such as working capital or operating expenses during this period. Furthermore there was an additional injection of funds through investment which helped increase the overall positive balance sheet position for Alpha Project at m12. This highlights potential growth opportunities for Alpha project going forward if they are able to secure further investments or loans in order to expand their operations further down the line.