

\subsection{Yearly Cash Flow}\label{sec:title}
\nonumsidenote{This section will analyze the yearly cash flow of Alpha Project from Year 1 to Year 5. We will discuss the sources and uses of cash, as well as the net income, operating cash flow, capital expenditures, and net cash balances for each year.}

The data in Table 1 provides a detailed look at Alpha Project's yearly cash flow from Year 1 to Year 5. In Year 1, Alpha Project had a net income of 8,814 dollars and an operating cash flow of 55,969 dollars. This was due to D&A expenses of 8,000 dollars being offset by wages and salaries paid out of 39155 dollars. Capital expenditures for this year were 150k from financing through shares and 0k through bank payments/loans. As a result, the company generated a negative net cash balance (-94k) but was able to offset it with investments totaling 150k. This resulted in an ending Cash Balance for Year 1 at 55,969 dollars. 

In subsequent years (Year 2-5), Alpha Project continued to increase its Net Income (+43k in Y2; +252k in Y3; +635K in Y4; +1M+ in Y5). Its Operating Cash Flow also increased significantly over time (+86K in Y2; +328K in Y3; +687K in Y4; +1M+inY5). The trend is attributed mainly to increasing D&A expenses (all 8K per year) which are more than offset by larger Wage & Salaries payments (-34666,-68606,-43651,-28042 respectively). Capital Expenditures decreased significantly over time (from 150K both via shares and bank loans/payments down to 0 across all categories). As such Net Cash Balances improved greatly over time (from -94K up until 2M+ by end of period). 

Overall these figures paint a positive picture for Alpha Projects' financial health as its Net Income increases steadily while its Operational Cash Flow improves exponentially thanks largely due to decreasing CAPEX costs over time. Furthermore it's impressive that despite large amounts spent on Wages & Salaries each year they are still able to generate significant profits throughout the period under consideration here. 

Summary: This section analyzed Alpha Projects' yearly cash flow from Years 1-5 which showed increasing Net Income and Operating Cash Flow indicating improving financial health due mainly to decreasing CAPEX costs over time despite large Wages & Salaries payments each year resulting ultimately in very impressive profits throughout the period considered here.