

\subsection{Monthly Balance Sheet}\label{sec:title}
\nonumsidenote{Summary: This section provides an analysis of the monthly balance sheet for the Alpha Project. It discusses total assets, current assets, cash, accounts receivable, inventories, fixed assets, liabilities and equity. The analysis reveals that the company has been steadily increasing its total assets over the past year and that it has a healthy level of current assets. It also shows that it has a strong cash position and low levels of accounts receivable.}

The Alpha Project's monthly balance sheet provides insight into the financial health of the company. The table below outlines key data points from each month in 2020 (m = month; y = year). 

Assets are divided into two categories: current and fixed. Current assets include items such as cash and accounts receivable (A/R), while fixed assets include items such as inventories and long-term debt. Liabilities consist of both current liabilities (e.g., trade payables) and long-term debt. Equity consists of earnings plus shareholders' equity. 

The first column in the table displays total assets for each month in 2020; this figure increased steadily over time from $155,589 at m/y 0 to $163,668 at m/y 12. This steady increase indicates that the company is making prudent investments in its operations which are resulting in growth over time. 

The second column displays current assets for each month; this figure increased from $6256 at m/y 0 to $21668 at m/y 12 indicating an increase in liquidity over time which is beneficial for businesses operating on tight margins or with large expenses due soon after purchase or production costs have been incurred by them .  Additionally, there was a significant increase in cash holdings from $1647 at m/y 0 to $17060 at m/y 12 suggesting that either more money was being taken out of operations or investments were being made that resulted in more money coming into operations during this period - either way it indicates good fiscal management on behalf of Alpha Project’s management team .  
The third column displays A/R figures; these remained constant throughout all months indicating either no sales activity taking place or collection efforts were successful enough to keep A/R figures low regardless if sales activity took place during any given month .   Inventories also remained relatively constant throughout all months indicating efficient production process taking place within Alpha Project’s operations .  Fixed Assets increased slightly from $149333 at m/y 0 to 142000 at m / y12 indicating some investments were made into long term projects but not enough to significantly impact overall asset totals .   Liabilities decreased slightly from 4 855at my0 to 4855at my12 suggesting some payables may have been paid off but not enough to significantly affect overall liability totals .    Total Equity increased significantly from 150734at my0