\nonumsidenote{Summary}
The table provides assumptions for the Alpha Project, a prospective business idea. The assumptions include growth, inflation, packing and shipping costs, material cost, maintenance cost, sales and marketing expenses, taxes, total revenue for five years with its maximum value in that period. Total net income after tax (NIAT) for five years with its maximum value in that period is also provided. Additionally, the minimum investment required is included along with NPV@10% and IRR.

Alpha Project has assumed an 80% growth rate over time. This assumption may be overly optimistic as it does not consider market saturation or competition. Inflation is expected to increase by 3%, which could lead to higher operating costs. Packing and shipping costs are estimated at 1%, while material costs are expected to increase by 1%. Maintenance costs are estimated at 0.5%, which may be reasonable if proper maintenance practices are implemented.

Other negative recoveries have been estimated at 0.25%. These estimates should be analyzed further to determine what factors contribute to these losses and how they can be minimized or eliminated altogether.

Sales and marketing expenses are expected to account for approximately 3% of total revenue over time. This estimate seems reasonable given the need for advertising and promotion efforts in most businesses.

Taxes will account for approximately 20% of total revenue over time. It is important to note that this estimate assumes no changes in tax laws or regulations during the five-year projection period.

Total revenue for five years is projected to reach $13,834,026 with a maximum revenue of $6,500,492 within that same timeframe. While these projections seem promising on paper; they do not necessarily guarantee success in reality without considering market realities

Total net income after tax (NIAT) for five years is projected at $2,069283 with a maximum NIAT of $1,129810. These projections seem reasonable and achievable if the assumptions made in other areas hold true.

The minimum investment required for the Alpha Project is $148,353. This estimate should be analyzed further to determine what factors contribute to this cost and how it can be minimized or eliminated altogether.

NPV@10% is estimated at $2,543,467.76 with an IRR of 186%. These estimates indicate that the Alpha Project could potentially be a profitable venture. However, these estimates are based on assumptions that may not hold true in reality without proper market analysis and competition research.