

\subsection{Yearly Profit and Loss}\label{sec:title}
\nonumsidenote{This report provides an analysis of the yearly profit and loss for Alpha Project. It includes a summary of revenues, product sales, cost of goods sold, gross profit, operating expenses, EBITDA margin, EBIT margin and net income margin. This report also provides insight into how these figures have changed over the course of the year.}

The table provided contains data regarding Alpha Project's performance over the course of a year. The table shows monthly revenue (in US dollars) as well as other associated costs such as cost of goods sold (COGS), gross profit, operating expenses and taxes. 

Revenue for Alpha Project has increased steadily over the course of the year from 601200 US dollars in month 0 to 6500492 US dollars in month 5. This increase is mirrored by product sales which have also increased from 601200 US dollars in month 0 to 6500492 US dollars in month 5. Other services remain at 0 throughout each month indicating that there are no other sources of revenue for Alpha Project besides product sales. 

Costs associated with running Alpha Project have also increased over the course of the year with COGS increasing from 237000 US dollars in month 0 to 2800188 US dollars in month 5. Labor costs are consistently higher than rent costs with labor costs increasing from 264000 US dollars to 1746750 US dollars while rent costs only increase from 30000 to 155000 during this period. Material and maintenance costs remain relatively constant at 6000-11124US$ per month respectively however other expenses such as IT and Sales \& Marketing have seen increases throughout this time period rising from 3600-4500US$ for IT and 18000-212673US$ for Sales \& Marketing respectively between months 0-5 . 

 Gross profit has decreased slightly over this time period decreasing from 364200US$ to 3700303US$. Operating expenses have followed a similar trend decreasing slightly from 337143US$ to 2279333US$. EBITDA has seen an overall increase during this time period rising form 19017US$ in Month 0 to 1420300US$ in Month 5 while EBIT margins have risen slightly form 11017US$ to 1412300USD$. Net income margins were 1.47\% in Month 0 but rose steadily throughout the year reaching 1738\% by Month 5 indicating that despite increasing operational costs profits are still on an upward trajectory due mainly to increasing revenues generated through product sales. 

Overall it can be seen that revenues generated through product sales continue to rise while associated operational costs remain relatively constant or decrease slightly resulting in steady increases across all profitability metrics including gross profit margins (6058\%-5692\%), EBITDA Margins (316\%-2185\%) ,EBIT Margins(183\%-2173\)and Net Income Margins(147\-17