

\subsection{Monthly Balance Sheet for Alpha Project}\label{sec:title}
\nonumsidenote{This section provides an analysis of Alpha Project's balance sheet data for the months January through December. This data shows that total assets and liabilities have increased steadily over the year, with current assets increasing more than long-term debt. The total equity has also increased, due to earnings from operations. Equity shareholders remain constant at 150,000.}

Alpha Project's balance sheet data for the months January through December is shown in Table \ref{tab:balance_sheet}. This table shows that total assets and liabilities have increased steadily over the year, with current assets increasing more than long-term debt. In particular, cash and inventories both increased significantly throughout the year while accounts receivable remained unchanged. Fixed assets also saw a slight increase due to new investments in equipment and infrastructure. 

Current liabilities also saw an increase throughout the year as trade payables and other payables rose slightly each month while provisions stayed constant at 118 dollars. Long-term debts remained unchanged throughout the year as there were no additional loans taken out by Alpha Project during this period. 

The total equity of Alpha Project also increased steadily over the course of the year due to earnings from operations which grew from 734 dollars in January to 8,814 dollars in December. Despite this growth, equity shareholders remained constant at 150,000 throughout this period indicating that these funds were reinvested back into Alpha Project rather than distributed among shareholders as dividends or bonuses. 

Overall these results show that Alpha Project was able to maintain a steady financial position throughout 2020 despite economic uncertainty caused by COVID-19 pandemic thanks to careful management of its finances and strategic reinvestment of its profits back into its operations rather than distributing them among shareholders as dividends or bonuses