

\subsection{Monthly Profit and Loss}\label{sec:title}
\nonumsidenote{This section provides a summary of the monthly profit and loss for the Alpha Project. It shows that revenue, product sales, and cost of goods sold remain consistent each month. Operating expenses are also steady, with labor costs, rent, material costs, maintenance costs, other expenses (negative recoveries) IT expenditures and sales/marketing expenses all being relatively consistent. Lease fees have remained at $670 per month. EBITDA is $1,585 each month while EBIT is slightly lower at $918 due to depreciation and amortization charges. Net income after taxes is $734 per month.}

The table provided shows the monthly profit and loss for the Alpha Project over twelve months. The data reveals that revenue sources remain consistent throughout this period with both product sales and general services contributing equally to total revenues of \$50,100 each month (row 1). Cost of goods sold has been steady at \$19,750 each month (row 4), resulting in a gross profit margin of 60.58\% (row 22). 

Operating expenses have also been relatively constant throughout this period (row 6). Labor costs account for the largest portion at \$22,000 per month (row 7), followed by rent payments of \$2,500 per month (row 8), material costs totaling \$500 per month (row 9), maintenance costing an additional \$500 per moth( row 10) as well as other non-recoverable expenses amounting to \$125 per moth( row 11). IT expenditure totals \$300 each moth( row 12) while marketing/sales expenditure amounts to \$1,500 every moth( row 13). Lastly lease fees contribute an additional expense of \$670 every moth( row 14). 

EBITDA for this period was calculated as 1.585 million dollars or 3.16\% margin on total revenues (rows 15-23). This number was reduced slightly by depreciation and amortization charges which resulted in an EBIT figure of 918 thousand dollars or 1.83\% margin on total revenues.(rows 16-24) After accounting for interest payments which totaled 0 dollars throughout this period (rows 18-25), taxes were applied resulting in a net income figure of 734 thousand dollars or 1.47\% margin on total revenues.(rows 20-25) 

Overall these figures suggest that the Alpha Project has been profitable over this twelve months period despite relatively high operating expenses due to strong gross profits margins achieved from its products/services sales activities