

\section{Monthly Profit and Loss}\label{sec:title}
\nonumsidenote{This section presents an analysis of the monthly profit and loss for Alpha Project. Revenue, product sales, cost of goods sold, gross profit, operating expenses, labor costs, rent, material costs, maintenance costs, other expenses (negative recoveries), IT costs, sales and marketing costs and lease fees are all taken into consideration when calculating the EBITDA (earnings before interest taxes depreciation and amortization), EBIT (earnings before interest and taxes), interest paid out on loans or investments made by Alpha Project as well as current tax payments. The resulting net income is then displayed in a table.}

The table presented in this section displays the monthly performance of Alpha Project from January to December. Revenue for each month is consistent at \$50 100 while product sales remain unchanged at \$50 100. There are no other services provided by Alpha Project so this figure remains at zero throughout the period. Cost of goods sold was also consistent at \$19 750 per month with a gross profit margin of 60.58\%. Operating expenses consist mainly of labor cost at \$22 000 per month followed by rent payments at \$2 500 per month. Material cost stands at \$500 while maintenance cost is also set to \$500 each month with other expenses (negative recoveries) amounting to only \$125 per month. IT services come in slightly higher than these figures standing at \$300 while sales and marketing is slightly higher still with a bill of  \$1 500 each month. Lease fee stands lowest out of all these figures totaling only 
\$670 each month. 

The total operating expense figure comes to just over 28 000 per months which leaves a healthy EBITDA margin of 3 16\%. This figure drops further when accounting for depreciation and amortization leaving an EBIT margin of 1 83\% but rises again once interest payments are factored in due to there being no loans or investments made during this period so that number remains constant throughout the year-long period analyzed here. Current tax payments stand at 184 per months leaving a net income margin just under 1 5\% for Alpha Project during this time frame making it clear that there is room for improvement if Alpha Project wishes to increase their profits moving forward into 2021 and beyond.. 

In summary, this section presented an analysis on the monthly profit & loss data for Alpha project from January - December 2020 showing revenue & product sales remain constant whilst most operating expenses remain relatively low apart from labor & rent costs which account for most expenditure with current tax payment coming in lowest amongst them all leaving a net income margin just under 1 5%.