

\subsection{Monthly Balance Sheet}\label{sec:title}
\nonumsidenote{This section provides a summary of the monthly balance sheet for Alpha Project. The table data shows that total assets increased from 155,589 in month 0 to 163,668 in month 12. Current assets increased from 6,256 to 21,668 over the same period. Cash increased from 1,647 to 17,060 and inventories increased from 4,608 to 4,608. Fixed assets decreased from 149,333 to 142,000 over the same period. Total liabilities and equity remained consistent throughout the twelve months at 155,589 - 163,668 while current liabilities stayed constant at 4,855 with trade payables increasing slightly from 812 to 812 and other payables increasing slightly from 3,925 to 3,925 with provisions remaining unchanged at 118 throughout all months. Long term debt was not reported in this table data set. Total equity increased by 814 over the twelve months while earnings increased by 814 as well.}

Alpha Project's monthly balance sheet reveals a steady increase in total assets over the twelve-month period studied here (from 155 589 in month 0 up to 163 668 in month 12). This growth can be attributed mainly to increases in current assets (from 6 256 up to 21 668) and cash (from 1 647 up to 17 060). Inventories also showed an increase of 4 608 units during this time frame but remained constant thereafter. Fixed assets were observed decreasing steadily over these twelve months (149 333 down till 142 000). 

Total liabilities and equity have remained relatively consistent throughout this period (155 589 - 163 668) with current liabilities staying constant at 4 855 units while trade payables have only seen a slight increase of 812 units during this time frame as well as other payables increasing slightly from 3 925 up till 3 925 with provisions remaining unchanged at 118 throughout all months studied here. Long term debt was not reported within this dataset however total equity has risen by 814 units whereas earnings have also seen an increase of 814 units respectively too which is likely due largely due towards investments made into Alpha Project's business operations such as marketing or research & development initiatives undertaken by management team members during this period under review here. 

Overall it appears that Alpha Project has experienced positive financial results overall judging by their balance sheet performance over these past twelve months which is encouraging news for investors who may be interested in investing into Alpha Projects future business operations going forward into 2021 and beyond!