

\subsection{Monthly Cash Flow}\label{sec:title}
\nonumsidenote{This section provides an overview of the monthly cash flow of Alpha Project from the data provided in the table. It explains how net income, depreciation and amortization, working capital, capital expenditure, bank payment/loan, and investment affect the cash balance over a period of twelve months.}

The table shows that Alpha Project's net income is constant at \$734 million for all 12 months. The company's depreciation and amortization (D&A) expenses are also constant at \$667 million throughout this period. Working capital ($WC$) is negative in month 0 but remains zero for all other months. Operating cash flow (OCF) is calculated as net income + D&A - WC which comes to \$1,647 million in month 0 and \$1,401 million for all other months. 

Capital expenditure (CapEx) affects OCF by increasing or decreasing it depending on whether it comes from funding sources such as banks or shareholders. In this case there is no CapEx from bank payments or loans during any of the 12 months so OCF remains unchanged at \$1,401 million throughout this period. However there is CapEx from shareholder funding with a one-time expense of \$150 million in month 1 which reduces OCF to zero for that month only; for all other months OCF remains unchanged at \$1,401 million due to no further CapEx being incurred during these periods. 

Net cash is calculated as OCF - CapEx which equals -\$148353 in month 0 due to the large one-off expense incurred by shareholders; however this figure increases steadily each month until it reaches a positive balance of \$170600 in month 12 due to no further CapEx being incurred after month 1. Investment also affects cash balance with a one-time injection of funds worth \$150 million occurring in month 1; this brings total cash up to a positive balance of \$164700 which increases steadily over time until it reaches its highest point of \$170600 in month 12 due to no additional investments being made after this point. 

In summary, Alpha Project's monthly cash flow was affected by net income remaining steady throughout this period while D&A expenses were also constant; working capital remained zero each month while operating cash flow was reduced by one-off shareholder capital expenditure during Month 1 only; net cash decreased significantly during Month 0 but increased steadily afterwards reaching its highest point at Month 12 when investment stopped and no further Capital Expenditure was incurred; overall total cash increased over time reaching its highest point at Month 12 when investment stopped and no further Capital Expenditure was incurred.