

\subsection{Monthly Profit and Loss for Alpha Project}\label{sec:title}

\nonumsidenote{Summary: The following section provides a detailed analysis of the monthly profit and loss data for Alpha Project. It includes an overview of total revenue, cost of goods sold, gross profit, operating expenses, labor costs, rent costs, material costs, maintenance costs, IT costs, sales and marketing expenses and lease fees. Additionally it provides insights into EBITDA margin and net income margin.} 

The table below shows the monthly profit and loss data for Alpha Project over a twelve-month period. The table contains information on total revenue earned by the company in each month along with other key financial metrics such as cost of goods sold (COGS), gross profit (GP), operating expenses (OE) and net income (NI). Additionally it provides insights into EBITDA margin and net income margin. 

Revenue was consistent throughout the year at \$50,100 per month. This is likely due to Alpha Projects focus on providing services rather than selling products or merchandise as there were no other service revenues reported during this period. Cost of Goods Sold totaled \$19750 per month which resulted in a Gross Profit Margin of 60.58%. Operating Expenses totaled \$28095 per month which included Labor Costs at \$22000 per month; Rent at \$2500; Material Costs at \$500; Maintenance Costs at \$500; Other Negative Recoveries at \$125; IT Costs at \$300; Sales & Marketing Expenses at \$1500; Lease Fees at \$670 resulting in an EBITDA Margin of 3.16% 	and an EBIT Margin of 1.83%. Interest was not reported during this period so Earnings Before Tax (EBT) equaled Earnings Before Interest & Taxes (EBIT). Current Tax amounted to 184 resulting in Net Income Margin amounting to 1.47%. 

 Overall these results indicate that Alpha Projects is generating consistent revenue but has yet to reach profitability due to high operating expenses when compared to its total revenue generated each month. To reach profitability they will need to reduce their overall operating expenses or increase their revenues through new services or product offerings.