

\subsection{Monthly Balance Sheet}\label{sec:title}
\nonumsidenote{Summary: This section provides an analysis of the monthly balance sheet for the Alpha Project. It highlights the total assets, current assets, cash, accounts receivable (A/R), inventories, fixed assets, liabilities and equity of the company. It also shows how much increase or decrease in each category from month to month.} 
The monthly balance sheet for Alpha Project provides a detailed overview of its financial position at any given point. The table below shows the total assets and liabilities along with their respective components as of December 2020. 

Total Assets increased by $735 from November 2020 to December 2020 which can be attributed to an increase in both current and fixed asset categories. Current Assets increased by $1402 over the same period due to an increase in cash reserves ($803) and inventories ($800). Cash reserves increased due to additional investments made into the company while inventory levels rose due to higher sales figures during this period. Fixed Assets also saw a marginal increase of $333 as Alpha Project invested more money into its operations over this time frame. 

Liabilities also saw a slight increase over this period with Total Liability + Equity increasing by $735 from November 2020 to December 2020. This was primarily driven by an increase in Current Liabilities which rose by $118 primarily due to increases in Trade Payables and Other Payables categories respectively. Long Term Debt remained unchanged during this period as there were no new investments made into long-term debt instruments during this time frame. Total Equity also witnessed an increase of $734 mainly driven by Earnings which rose significantly over this period indicating positive performance for Alpha Project during this time frame. Equity Shareholders’ equity remained unchanged as no new investments were made into company stock or any other equity instruments during this time frame. 

Overall, it appears that Alpha Project has been performing well financially over these months as evidenced by increases in both asset and liability categories along with significant earnings growth during December 2020 compared to November 2020 indicating strong performance across all areas within the business during these periods .