

\nonumsidenote{\textbf{Summary:} This chapter presents the yearly cash flow of the Alpha Project company. The net income increases each year, while D&A and WC remain constant. The operating cash flow is positive in all years, with an increase from 55,969 to 1,165,852 over five years. CAPEX is mainly funded by shareholders’ investment and there are no bank payments or loans during this period. As a result, the cash balance also increases significantly from 55,969 to 2,198,403.}

The Alpha Project company's Yearly Cash Flow can be seen in the table above. In this chapter we will analyze the data presented in order to gain insight into the financial health of the company over time. 

Starting with Net Income for year 1 (y1), it is 8,814 which increases steadily over time to 1,129,810 by year 5 (y5). This indicates that the Alpha Project has been successful at increasing its profits year on year which is a positive sign for investors and stakeholders alike. 

Depreciation and Amortization (D&A) remains constant throughout all five years at 8000 indicating that there have been no significant investments or changes made in terms of capital expenditure or asset acquisition/disposal during this period. 

Wages and Compensation (WC) remain relatively stable between y1-y4 before dropping significantly for y5 as seen in column 3 of the table. This could indicate that either staff costs were reduced due to cost cutting measures or alternatively that more staff were employed during y1-y4 than was necessary resulting in lower wages costs for y5 after restructuring had taken place.  

Operating Cash Flow (OCF) shows a steady increase from 55,969 to 687 060 between y1-y4 before jumping significantly to 1 165 852 for y5 indicating strong growth potential within this business sector as well as healthy profits being generated through operations each year despite changes in wages costs incurred during this period. 

 Capital Expenditure (CAPEX) is mainly funded by Shareholder Investment with 150000 invested initially followed by 25000 invested one year later but no further investments thereafter indicating that any additional capital expenditure needs have been met through other means such as retained earnings or debt financing rather than additional equity investment since then - although it should be noted that further equity investments could still be made if required at any point moving forward should funding become an issue again later down line..  

 Cash Flow From Bank Payment/Loan remains zero throughout all five years meaning either these have not been used as sources of finance or alternatively they may have already been paid back prior to these figures being reported - however it should be noted here that if needed then bank financing could still be used going forward should other forms of finance become unavailable at any stage moving forward..  

 Finally Net Cash shows a negative value (-94 031) initially which then reduces gradually until becoming positive (+687 060 ) by y4 before increasing substantially (+1 165 852 ) for y5 showing how much healthier their finances are now compared with previous years when losses were incurred initially due largely thanks largely due increased profits achieved through operations combined with shareholder investments made earlier on..   

 Overall these figures show how successful Alpha Project has become financially over time thanks largely due increased profits achieved through operations combined with shareholder investments made earlier on - thus making them far more attractive proposition now compared with what they once were just few short years ago when losses were incurred initially..