

\subsection{Monthly Balance Sheet: m/y}\label{sec:title}
\nonumsidenote{Summary: This section provides an analysis of Alpha Project's balance sheet for the month of m/y. It includes a breakdown of assets and liabilities, as well as an overview of current assets, cash, accounts receivable, inventories, fixed assets and long-term debt. Additionally, it provides information on total liability and equity, current liability and trade payables, other payables and provisions. Finally, it also outlines equity shareholders' earnings.} 

Alpha Project's monthly balance sheet for the month of m/y is provided in Table \ref{tab:monthlybalancesheet}. The table shows that the company has total assets amounting to \$155,589 in the beginning of the month which increases to \$163,668 by the end. The increase is attributed to both current assets as well as fixed assets which have increased from \$6256 at the start of the month to \$21 668 by its end. Current Assets are mainly composed of cash (\$1 647 - 17 060), accounts receivable (0) and inventories (4 608 - 4 608). Fixed Assets have increased from 149 333 to 142 000 over this period due to new investments made into capital equipment or land improvements. 

The company’s liabilities are composed mainly of Total Liability + Equity (\$155 589 - 163 668) with Trade Payables (812 - 812), Other Payables (3 925 - 3 925) and Provisions (118 - 118). Long Term Debt remains unchanged over this period at 0. Total Equity stands at 150 734 increasing steadily up until 158 814 by the end of this period while Earnings increase from 734 up until 8 814 during this same time frame. Lastly Equity Shareholders remain constant during this period at 150 000 indicating that there has been no change in ownership structure during these months. 

Overall Alpha Projects’ financial position appears stable with a steady growth in both their Assets and Liabilities over this period indicating healthy levels liquidity and solvency respectively. Their Cash Flow position is also strong with no changes being observed in either their Long Term Debt or Equity Shareholders positions suggesting that all funds required for operations have been secured internally without any external financing being necessary during these months. 

