

\subsection{Yearly Profit and Loss}\label{sec:title}
\nonumsidenote{This section provides an analysis of the yearly profit and loss data for the Alpha Project. It examines the total assets, current assets, cash, accounts receivable, inventories, fixed assets, liabilities, total liability plus equity, current liabilities, trade payables, other payables and provisions. The long-term debt is also discussed to provide a complete overview of the company's financial position.}

The table data shows that in year 0 (y0), Alpha Project had total assets amounting to 207 708 USD with 65 708 USD in current assets. Cash accounted for 55 969 USD while accounts receivable (A/R) was zero. Inventories were 9 740 USD while fixed assets amounted to 142 000 USD. Liabilities were not specified but total liability plus equity was equal to 207 708 USD with 48 895 USD in current liabilities and 379USD in trade payables as well as 47 103USD in other payables and 1 413USD in provisions. Equity shareholders held 150 000USD worth of earnings at this time. 

In y1 there was a significant increase in both total and current assets which reached 319 071USD and 35 071USD respectively due mainly to an increase in cash from 55 969 to 17 014USD as well as increases in inventories from 9 740 to 18 057USD and fixed assets from 142 000to 284 000USD respectively. Total liability plus equity increased accordingly reaching 319071USd with 91 878USd worth of current liabilities including 379USd of trade payables 88 835USd of other payables 2 665 USd worth of provisions as well as 175000 USd held by equity shareholders 

In y2 there was another large increase with total asset reaching 654 969 US dollars while cash increased again this time reaching 345 491 US dollars along with 33 479 US dollars worth of inventories 276000 US dollars worth of fixed asset 91 878 US dollar worth of provision 5 112US dollar worth of provision Long term debt is not specified but it should be assumed that it remained constant between years two and three 

 In y3 Total Assets reached 1 362 620 Dollars Current Assets rose significantly from 378969 Dollars up to 1094 620 Dollars Cash also rose significantly from 345 491 Dollars up To 1 032 551 Dollars Accounts Receivable remain at zero Inventories increased slightly From 33 479 Dollar To 62 069 Dollar Fixed Assets decreased Slightly From 276000 Dollar To 268000 Dollar Liabilities are not specified but Total Liability Plus Equity remains constant at 1362 620 Dollar Current Liability decreased slightly From 248 147 Dollar To 240552 Dollar Trade Payable And Other Payable remain constant At 379 And 240552 Dollar Respectively Provisions decreased slightly From 7 217Dollar To 62069Dollar Long Term Debt is still Not