

\subsection{Yearly Profit and Loss}\label{sec:title}
\nonumsidenote{This section provides a summary of the yearly profit and loss for Alpha Project. It includes an analysis of the total assets, current assets, cash, accounts receivable (A/R), inventories, fixed assets, liabilities, current liabilities, trade payables, other payables, provisions, long-term debt and equity shareholders' earnings.}

The table provided shows the total assets for Alpha Project across five years. In year 0 (207 708 USD) and year 1 (319 071 USD) there is a noticeable increase in total assets due to additional investments made by shareholders. This trend continues into years 2 (654 969 USD), 3 (1 362 620 USD) and 4 (2 573 479 USD). 

Current Assets also increased over time from 65 708 USD in year 0 to 35 071 in year 1 and then 378 969 in year 2. Cash remains relatively stable at 55 969 USD until it increases significantly to 17 014 in year 1 followed by 345 491 in year 2. Accounts Receivable remain zero throughout all five years as do Inventories which range from 9 740 - 18 057.  Fixed Assets remain consistent at 142 000 - 284 000 across all five years with a slight decrease from 284 000 to 276 000 between years 1-2 respectively. 

Liabilities have remained relatively constant since the first two years with Total Liability + Equity remaining at 207 708 - 319 071 respectively before increasing significantly to 654 969 in Year 2 onwards up until Year 4 when it reached its peak of 2 573 479 before decreasing slightly again to 2 244 283 in Year 5. Current Liabilities show similar trends starting off low at 48 895 - 91 878 before reaching their peak of 248 147 during Year 3 followed by 329 196 during Year 5 whilst Trade Payables remain constant at 379 throughout all five years as do Other Payables ranging from 47 103 - 88 835 across all five years except for 240 552 during Year 3 followed by 319 240 during Year 5. Provisions also increase steadily over time ranging from 1413 - 2665 during Years 0-1 respectively before peaking at 11 577 during Year 4 only to drop back down again slightly to 9577 during the final year. Long Term Debt remains zero throughout all five years as well as Equity Shareholders’ Earnings which range from 8 814 - 52 193 except for 304 064 during Year 2 and finally peaking at 2069 283 during the last financial period ending on December 31st 2020 . 

In conclusion Alpha Project has seen steady growth over time with Total Assets increasing considerably each financial period whilst Current Assets have been fluctuating more frequently but still showing positive signs of growth overall thanks mainly due to investment made by shareholders alongside other factors such as Cash Flow Management etc… Liabilities have been