

\subsection{Assumptions}\label{sec:assumptions}
\nonumsidenote{Summary: This section provides an analysis of the assumptions used to calculate the Total Revenue and Net Income After Tax (NIAT) for Alpha Project over a five year period. The assumptions include growth, inflation, packing and shipping, material cost, maintenance cost, other costs (neg. recoveries), sales and marketing expenses and taxes. The results of this analysis show that Alpha Project can expect to generate a total revenue of $13,834,026 over five years with a maximum revenue of $6,500,492 in any given year; while NIAT is expected to be $2,069,283 with a maximum amount of $1,129,810 in any one year. A minimum investment of $148353 is required to realize these returns.}

Alpha Project's business plan requires an analysis of the assumptions used to calculate their Total Revenue and Net Income After Tax (NIAT) for the next five years. To properly analyze these assumptions we must first understand what each assumption represents. Growth is defined as the rate at which Alpha Project expects its revenues or profits will increase during this period; inflation is calculated as an average annual percentage change in prices; packing and shipping are costs associated with packaging goods for shipment; material cost refers to raw materials needed for production; maintenance cost covers repairs or updates needed on equipment or facilities; other costs refer to any negative recoveries that may occur during production such as discounts given on products or services sold; sales and marketing expenses cover advertising campaigns or promotions run by Alpha Project; finally taxes incur payments made by Alpha Project based on their profits earned during the period. 

With these definitions in mind we can now analyze our table data which shows us that Alpha Project expects growth at 80\%, inflation at 3\%, packing and shipping at 1.00\%, material cost at 1.00\%, maintenance cost at 0.50\%, other costs (neg. recoveries) at 0.25\%, sales and marketing expenses at 3.00\% and taxes incurred will be 20%. Based on these assumptions our table data shows us that if all goes according to plan then after five years Alpha Projects total revenue will be 13 834 026 US dollars with a maximum revenue 6 500 492 US dollars in any one year while NIAT will be 2 069 283 US dollars with a maximum amount 1 129 810 US dollars in any one year respectively. In order for these returns to be realized there needs to be an initial investment of 148 353 US dollars followed by investments throughout the duration of 5 years until all calculations have been completed successfully.. 

In conclusion our analysis shows that if all goes according to plan then Alpha Projects total revenue should reach 13 834 026 US dollars over 5 years while NIAT should reach 2 069 283 US dollars within those same 5 years provided they make a minimum initial