

\subsection{Yearly Profit and Loss}\label{sec:title}
\nonumsidenote{This section provides an analysis of the yearly profit and loss for Alpha Project. It includes a summary of total assets, current assets, cash, accounts receivable (A/R), inventories, fixed assets, liabilities, current liabilities, trade payables, other payables, provisions and long-term debt. Additionally it covers total equity and earnings as well as equity shareholders.}

The table data provided in this section shows the yearly profits and losses for Alpha Project from 0 to 5 years. The first column represents the year while the following columns represent the corresponding values for each year. The Assets row shows that Total Assets have increased steadily over five years with a value of 207708 in Year 0 to 2573 479 in Year 5. This indicates that Alpha Project has been able to increase its asset base over time which is a positive sign for any business. 

Current Assets have also increased steadily from 65708 in Year 0 to 2313479 in Year 5 indicating that Alpha Projects’ liquidity position has improved over time. Cash has increased significantly from 55969 in Year 0 to 2198403 in Year 5 showing that Alpha Projects’ ability to generate cash has improved significantly over time. Accounts Receivable (A/R) remain unchanged throughout all five years at zero indicating there were no outstanding receivables during this period which is a positive sign as it means all invoices were paid promptly by customers on due date without any delays or defaults. Inventories have also increased steadily from 9740 in Year 0 to 115076 in Year 5 showing an improvement both in terms of sales volume and inventory management efficiency over time. 

Fixed Assets have decreased slightly but remained fairly consistent across all five years ranging between 142000 - 260000 indicating that investments into fixed assets such as property plant & equipment (PPE) was not significant during this period but still managed effectively with minimal wastage or depreciation costs incurred resulting from poor maintenance or obsolescence issues associated with PPEs owned by Alpha Project.. 
Liabilities show no data available across all five years indicating there were no borrowings made during this period which could be attributed either due to sufficient internal funds generated through operations or external funds raised through venture capital investment sources if any..  Total Liability + Equity follows a similar trend as Total Assets increasing steadily from 207708 - 2573 479 across all five years indicating that liabilities did not increase significantly during this period but instead were kept under control without compromising on equity capital requirements necessary for growth initiatives taken up by Alpha Project..   Current Liability also follows a similar pattern increasing steadily ranging between 48895 - 329196 across all five years suggesting some level of borrowings taken up but managed efficiently without creating any significant burden on the company's finances or operations..   Trade Payables remain unchanged at 379 across all five years showing prompt payment made